### 2021-12-13 manuscript/manuscript.Rmd
first commit

---
title: "Untitled"
output: github_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

```{r setup, include=FALSE}
library("worcs")
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
# load_data()
knitr::opts_chunk$set(echo = TRUE)
```

This manuscript uses the Workflow for Open Reproducible Code in Science [@vanlissaWORCSWorkflowOpen2020] to ensure reproducibility and transparency. All code <!--and data--> are available at <git@github.com:cjvanlissa/srma_fearlearning.git>.

This is an example of a non-essential citation [@@vanlissaWORCSWorkflowOpen2020]. If you change the rendering function to `worcs::cite_essential`, it will be removed.

<!--The function below inserts a notification if the manuscript is knit using synthetic data. Make sure to insert it after load_data().-->
`r notify_synthetic()`

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-12-13 codebook_dat.Rmd
add data

---
title: "Codebook created on 2021-12-13 at 2021-12-13 15:15:29"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = 'asis')
```

A codebook contains documentation and metadata describing the contents, structure, and layout of a data file.

## Dataset description
The data contains 295 cases and 15 variables.

## Codebook

```{r}
summaries <- read.csv("./codebook_dat.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### Legend

* __Name__: Variable name
* __type__: Data type of the variable
* __missing__: Proportion of missing values for this variable
* __unique__: Number of unique values
* __mean__: Mean value
* __median__: Median value
* __mode__: Most common value (for categorical variables, this shows the frequency of the most common category)
* **mode_value**: For categorical variables, the value of the most common category
* __sd__: Standard deviation (measure of dispersion for numerical variables
* __v__: Agresti's V (measure of dispersion for categorical variables)
* __min__: Minimum value
* __max__: Maximum value
* __range__: Range between minimum and maximum value
* __skew__: Skewness of the variable
* __skew_2se__: Skewness of the variable divided by 2*SE of the skewness. If this is greater than abs(1), skewness is significant
* __kurt__: Kurtosis (peakedness) of the variable
* __kurt_2se__: Kurtosis of the variable divided by 2*SE of the kurtosis. If this is greater than abs(1), kurtosis is significant.

This codebook was generated using the [Workflow for Open Reproducible Code in Science (WORCS)](https://osf.io/zcvbs/)

### 2021-12-13 prepare_data.R

@@ -4,3 +4,37 @@
 # to store the data.
 
 library(worcs)
+library(readxl)
+library(tidySEM)
+dat <- readxl::excel_sheets("SR_SSRI_FearLearning_ForestPlot_data_20211018_Caspar.xlsx")
+dat <- lapply(dat[-1], function(x){
+  tmp <- as.data.frame(readxl::read_xlsx(path = "SR_SSRI_FearLearning_ForestPlot_data_20211018_Caspar.xlsx", sheet = x))
+  names(tmp) <- tolower(names(tmp))
+  tmp[["remarks"]] <- NULL
+  tmp$Process = x
+  tmp
+})
+dat <- tidySEM:::bind_list(dat)
+open_data(dat)
+#   Information regarding this data file for the SR fear learning & SSRIs
+#
+# This data file is organised by fear learning process. This means that every fear learning process has its own Excel sheet.
+#
+# Within these sheets you find the same layout. The different columns are explained below:
+#
+#   Study name
+# Article code
+# Type of SSRI
+# Frequency
+# Disease induction
+# Species
+# Type of test
+# Sensitivity analysis
+#
+#
+#
+# Analyses we want to perform:
+#
+#   1. Separate meta-analyses of the five fear learning processes that have enough data (acq learn to cue, acq learn to ctx, acq retr to cue, acq retr to ctx, ext learn to cue)
+# 2. Subgroup analyses of the five factors (SSRI, frequency, disease induction, species, type of test) per fear learning process
+# 3. Check for multi collinearity

### 2021-12-13 manuscript/manuscript.Rmd
first analysis

@@
 title: "Untitled"
-output: github_document
+output: bookdown::html_document2
 date: '`r format(Sys.time(), "%d %B, %Y")`'
@@
 ```{r setup, include=FALSE}
+run_everything = FALSE
 library("worcs")
+library(metafor)
+library(ggplot2)
+library(kableExtra)
+library(tidySEM)
 # We recommend that you prepare your raw data for analysis in 'prepare_data.R',
@@
 # (whichever is available), to allow anyone to reproduce your code:
-# load_data()
+load_data()
+dat$Process <- ordered(dat$Process, levels = unique(dat$Process))
+processes <- levels(dat$Process)
+totaln <- dat[!duplicated(dat$article.code), c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group", "Process")]
+totaln <- sapply(processes, function(p){ sum(totaln[totaln$Process == p, -3], na.rm = TRUE)})
+
+dat <- escalc(measure = "SMD",
+         n1i = dat$number.of.animals.in.control.group,
+         n2i = dat$number.of.animals.in.intervention.group,
+         m1i = dat$mean.control.group,
+         m2i = dat$mean.experimental.group,
+         sd1i = dat$sd.control.group,
+         sd2i = dat$sd.experimental.group,
+         data = dat)
+# dat[c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group", "mean.control.group", "mean.experimental.group", "sd.control.group", "sd.experimental.group")] <- NULL
+dat <- dat[!is.na(dat$yi), ]
+zscores <- scale(dat[["yi"]])
+maxz <- max(zscores)
+dat <- dat[-which.max(zscores), ]
+dat$id_study <- as.integer(factor(trimws(gsub("\\(\\d+\\)$", "", as.character(dat$article.code)))))
+dat$id_es <- 1:nrow(dat)
 knitr::opts_chunk$set(echo = TRUE)
@@
 
-This manuscript uses the Workflow for Open Reproducible Code in Science [@vanlissaWORCSWorkflowOpen2020] to ensure reproducibility and transparency.
-All code <!--and data--> are available at <git@github.com:cjvanlissa/srma_fearlearning.git>.
+<!--   Information regarding this data file for the SR fear learning & SSRIs -->
 
-This is an example of a non-essential citation [@@vanlissaWORCSWorkflowOpen2020]. If you change the rendering function to `worcs::cite_essential`, it will be removed.
+<!-- This data file is organised by fear learning process. This means that every fear learning process has its own Excel sheet. -->
 
-<!--The function below inserts a notification if the manuscript is knit using synthetic data. Make sure to insert it after load_data().-->
-`r notify_synthetic()`
+<!-- Within these sheets you find the same layout. The different columns are explained below: -->
 
-## GitHub Documents
+<!--   Study name -->
+<!-- Article code -->
+<!-- Type of SSRI -->
+<!-- Frequency -->
+<!-- Disease induction -->
+<!-- Species -->
+<!-- Type of test -->
+<!-- Sensitivity analysis -->
 
-This is an R Markdown format used for publishing markdown documents to GitHub.
-When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
+<!-- Analyses we want to perform: -->
+<!-- 2. Subgroup analyses of the five factors (SSRI, frequency, disease induction, species, type of test) per fear learning process -->
+<!-- 3. Check for multi collinearity -->
 
-## Including Code
+```{r threelev, echo=FALSE, warning=FALSE, message=FALSE, results="hide", eval = run_everything}
+mlm <- lapply(processes, function(p){
+  df <- dat[dat$Process == p, ]
+  #Conduct meta-analyses
+  #model.mods <- rma.mv(yi, vi, random = list(~ 1 | id_study, ~ 1 | id_es), data=df) 
+  model.full <- rma.mv(yi, vi, random = list(~ 1 | id_study, ~ 1 | id_es), data=df) 
+  model.within_null <- rma.mv(yi, vi, random = list(~ 1 | id_study, ~ 1 | id_es), sigma2=c(NA,0), data = df) 
+  model.between_null <- rma.mv(yi, vi, random = list(~ 1 | id_study, ~ 1 | id_es), sigma2=c(0,NA), data = df) 
+model.both_null <- rma.mv(yi, vi, random = list(~ 1 | id_study, ~ 1 | id_es), sigma2=c(0,0), data = df) 
+#model.mods <- rma.mv(yi, vi, mods = as.formula(paste0("~ ", paste(moderators, collapse = " + "))), random = list(~ 1 | id_study, ~ 1 | id_es), data = df) 
+#ggplot(, aes(x=d, colour=interventioncode))+geom_density()
+#anova(model.full,rma.mv(yi, vi, mods = ~interventioncode, random = list(~ 1 | id_study, ~ 1 | id_es), data = df) ) 
+aov_within <- anova(model.full,model.within_null) 
+aov_between <- anova(model.full,model.between_null) 
+aov_bothnull <- anova(model.full,model.both_null) 
+aov_table <- data.frame(rbind(
+c(aov_between$fit.stats.f[c(3:4, 1)], LRT = NA, p = NA),
+c(aov_within$fit.stats.r[c(3:4, 1)], LRT = aov_within$LRT, p = aov_within$pval),
+c(aov_between$fit.stats.r[c(3:4, 1)], LRT = aov_between$LRT, p = aov_between$pval),
+c(aov_bothnull$fit.stats.r[c(3:4, 1)], LRT = aov_bothnull$LRT, p = aov_bothnull$pval)
+))
+rownames(aov_table) <- c("Three-level model", "Within-studies variance constrained", "Between-studies variance constrained", "Both variance components constrained")
+write.csv(aov_table, paste0("threelevel_ma_", p, ".csv"))
+confints <- confint(model.full)
+#CHeck convergence of variance components:
+#par(mfrow=c(2,1))
+#plot.profile1 <- profile(model.full, sigma2=1)
+#plot.profile2 <- profile(model.full, sigma2=2)
 
-You can include R code in the document as follows:
+#Write forest plot to file
+xname <- paste0("Hedges' g (", p, ")")
+tmp <- df[order(df$vi, decreasing = TRUE), ]
+df_es <- data.frame(
+    Study = ordered(tmp$article.code, levels = unique(tmp$article.code)),
+    y = 1:nrow(tmp),
+    es = tmp$yi,
+    lb = tmp$yi - 1.96*sqrt(tmp$vi),
+    ub = tmp$yi + 1.96*sqrt(tmp$vi),
+    Process = p)
 
-```{r cars}
-summary(cars)
+dfoverall <- data.frame(x = c(model.full$ci.ub, model.full$b[1,1], model.full$ci.lb, model.full$b[1,1]),
+                        y = c(max(df_es$y)+2, max(df_es$y)+2.5, max(df_es$y)+2, max(df_es$y)+1.5))
+
+pforest <- ggplot(data=df_es)+ 
+  geom_point(aes(y=y, x=es))+ 
+  geom_errorbarh(aes(y = y, xmin=lb, xmax=ub), height=.1)+
+
+  # geom_point(data=data.frame(y = max(df_es$y)+2, es = model.full$b[1,1]), aes(y=y, x=es), size=4, shape = 15, fill = "black")+ 
+  # geom_errorbarh(data = data.frame(y = max(df_es$y)+2, lb = model.full$ci.lb, ub = model.full$ci.ub), aes(y = y, xmin=lb, xmax=ub), height=.4, size = 2)+
+  geom_polygon(data = dfoverall, aes(x = x, y = y))+
+  scale_x_continuous(name=xname, limits = c(min(df_es$lb), min(c(10,max(df_es$ub)))))+
+  scale_y_continuous(name = "", breaks=1:max(df_es$y), labels = df_es$Study, trans="reverse")+
+  #adding a vertical line at the effect = 0 mark
+  geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
+  geom_hline(yintercept=max(df_es$y)+1)+
+  theme_minimal()
+
+ggsave(paste0("threelevel_ma_forest", p, ".png"), pforest, device = "png")
+res = data.frame(Variance = c("Overall ES", "V within", "V between"),
+                 rbind(c(estimate = model.full$b[1,1], ci.lb = model.full$ci.lb, ci.ub = model.full$ci.ub, model.full$pval),
+                       c(confints[[1]]$random[1,], aov_table$p[3]),
+                       c(confints[[2]]$random[1,], aov_table$p[2])))
+  list(mod = model.full,
+    aov_table = aov_table,
+       res = res)     
+})
+saveRDS(mlm, "mlm.RData")
+```
+```{r, include = FALSE}
+num_effect_sizes <- table(table(dat$article.code))
 ```
 
-## Including Plots
+## Descriptive statistics
 
-You can also embed plots, for example:
+The effect size estimates ranged from `r formatC(min(dat[["yi"]]), digits = 2, format = "f")` to `r formatC(max(dat[["yi"]]), digits = 2, format = "f")` ($M = `r report(mean(dat[["yi"]]))`, SD = `r report(sd(dat[["yi"]]))`$).
+One study had an effect size estimate more than standard deviations from the mean effect size ($Z = `r max(zscores)`$); it was removed as an outlier.
+Sample sizes ranged from `r min(rowSums(dat[, c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group")]))` to `r max(rowSums(dat[, c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group")]))` animals ($M = `r formatC(mean(rowSums(dat[, c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group")])), digits = 2, format = "f")`, SD = `r formatC(sd(rowSums(dat[, c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group")])), digits = 2, format = "f")`$).
+Several studies reported multiple effect sizes (`r min(names(num_effect_sizes)) ` - `r max(names(num_effect_sizes))`, with most reporting effect size).
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+## Meta-analysis
+
+Meta-analysis was conducted in R [@r_core_team_r:_2017-1] using the R-packages `metafor` [@viechtbauer_conducting_2010-1], and `pema` [@van_lissa_metaforest:_2017-1], following the recommendations of Field and Gillett (2010).
+
+## Three-level meta-analysis
+
+First, we used three-level meta-analysis to account for dependent effect sizes within studies [@van_den_noortgate_meta-analysis_2015].
+Let $y_{jk}$ denote the $j$ observed effect sizes $y$, originating from $k$ studies.
+The multi-level model is then given by the following equations: 
+<!--
+\begin{center}
+$\begin{equation}
+\left.
+\begin{aligned}
+y_i &= \theta_i + \epsilon_i &\text{where } \epsilon_i &\sim N(0, \sigma^2_i)\\
+\theta_i &= \mu + \zeta_i &\text{where } \zeta_i &\sim N(0, \tau^2)
+\end{aligned}
+\right\}
+\end{equation}$
+\end{center}
+-->
+
+$$
+      \left.
+      \begin{aligned}
+        y_{jk} &= \beta_{jk} + \epsilon_{jk} &\text{where } \epsilon_{jk} &\sim N(0, \sigma^2_{\epsilon_{jk}})\\
+        \beta_{jk} &= \theta_k + w_{jk} &\text{where } w_{jk} &\sim N(0, \sigma^2_{w})\\
+        \theta_{k} &= \delta + b_{k} &\text{where } b_k &\sim N(0, \sigma^2_{b})
+      \end{aligned}
+      \right\}
+$$
+
+The first equation indicates that observed effect sizes are equal to the underlying population effect size, plus sampling error $\epsilon_{jk}$.
+The second equation indicates that population effect sizes within studies are a function of a study-specific true effect size, plus within-study residuals $w_{jk}$.
+The third equation indicates that the distribution of study-specific true effect sizes are distributed around an overall mean effect, with between-study residuals $b_k$.
+
+Separate meta-analyses were conducted for each of the fear learning processes.
+The overall pooled effect sizes were:
+
+```{r, results = "asis"}
+mlm <- readRDS("mlm.RData")
+tb <- lapply(1:length(processes), function(i){
+  tb <- mlm[[i]]$res
+  tb$Process <- processes[i]
+  tb
+})
+tb <- do.call(rbind, tb)
+tb$CI <- tidySEM::conf_int(lb = tb$ci.lb, ub = tb$ci.ub)
+tb[c("ci.lb", "ci.ub")] <- NULL
+names(tb) <- c("Parameter", "Estimate", "p", "Process", "CI")
+kbl(tb[, c("Parameter", "Estimate", "CI", "p", "Process")], digits = 2)
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+The overall effect size estimate differed significantly from zero only for `r paste0(tb[tb$Parameter == "Overall ES", ]$Process[tb[tb$Parameter == "Overall ES", ]$p < .05], collapse = ", ")`.
+
+The within-studies variance component $\sigma^2_w$ (between effect sizes) was significant only for `r paste0(tb[tb$Parameter == "V within", ]$Process[tb[tb$Parameter == "V within", ]$p < .05], collapse = ", ")`.
+
+The between-studies variance $\sigma^2_b$ was significant for all processes, except `r paste0(tb[tb$Parameter == "V between", ]$Process[tb[tb$Parameter == "V between", ]$p > .05], collapse = ", ")`.
+
+This indicates that there was substantial heterogeneity between average effect sizes across studies, but not between effect sizes published within the same studies.
+
+## Moderator analyses
+
+Five moderators were coded: (SSRI, frequency, disease induction, species, type of test).
+The effect of these moderators was investigated using meta-regression.
+Because the within-studies variance component was non-significant in most three-level analyses,
+and because most studies only had one effect size, we dropped the third level in the moderator analyses.
+
+```{r}
+mods <- c("type.of.ssri", 
+"frequency", "disease.induction", "species", "type.of.test")
+# 
+# mlm <- lapply(processes, function(p){
+#   df <- dat[dat$Process == p, ]
+#   modmat <- model.matrix(~., df[mods])[,-1]
+#   zerocols <- colSums(modmat) == 0
+#   zero <- colnames(modmat)[zerocols]
+#   modmat <- modmat[, !zerocols]
+#   dupcols <- which(duplicated(as.list(data.frame(modmat))))
+#   dups <- colnames(modmat)[dupcols]
+#   modmat <- modmat[, !dupcols]
+# res <- rma(yi = df$yi,
+#            vi = df$vi,
+#            mods = modmat)
+#vifs <- vif(res)
+#})
+# res <- rma(yi = dat$yi,
+#            vi = dat$vi,
+#            mods = model.matrix(~., data[mods])[,-1])
+# vifs <- vif(res)
+
+# write.csv(vifs, "vif.csv")
+# worcs:::write_gitig(".gitignore", "!vif.csv")
+```
+
+<!-- 3. Check for multi collinearity -->
+
+```{r results="asis", eval = FALSE}
+apa_table(
+aov_table, caption = "Model fit and likelihood ratio tests", note = "Significance of variance components is assessed by constraining them to zero, and examining the significance of a log-likelihood (ll) ratio test (LRT) comparing the constrained model to the full three-level model.
+", placement = "p"
+)
+
+failsafe <- fsn(d, vi, data = data)
+```
+
+*A chi-square test of homogeneity of effect sizes was not significant, 2(19) 21.53, p=.37. These measures suggest considerable similarity in effect sizes across studies.*
+*Consistent with this finding, moderator analysis suggested that the effect of age or sex on the overall effect size was not significant.*
+
+```{r funnel_plot, echo=FALSE, warning=FALSE, message=FALSE, results="hide", eval = F}
+png(file="funnel_plot.png",width=148, height=105, units="mm", res = 300)
+funnel(model.full, main=NULL, 
+       back="white", shade="white", hlines="white", xlab = "Effect size (Cohen's d)")
+dev.off()
+cairo_pdf("funnel_plot.pdf", family="Helvetica", width = 5.8, height = 4.1)
+  funnel.rma(model.full, main=NULL, 
+       back="white", shade="white", hlines="white", xlab = "Effect size (Cohen's d)", digits = 2)
+dev.off()
+embed_fonts("funnel_plot.pdf", outfile="funnel_plot.pdf")
+beggstest <- regtest(data$d, data$vi)
+sd(data$age)
+```
+File drawer analysis [@rosenthal_file_1979] revealed that `failsafe[["fsnum"]]` unpublished, filed, or unretrieved studies averaging null results would be required to bring the average unweighted effect size to nonsignificance.
+Visual inspection of the Funnel plot (Figure 3) did not clearly indicate asymmetry, which could be a sign of publication bias.
+Begg's test of funnel asymmetry (based on random-effects meta-analysis) similarly did not indicate significant bias, $Z = ` formatC(beggstest[["zval"]], digits = 2, format = "f")`$, $p = `formatC(beggstest[["pval"]], digits = 2, format = "f")`$.
+
+## Moderation
+
+We coded several potential theoretical and methodological moderators: Proportion of male participants, average age of the sample, type of population (typical or socially anxious), type of intervention, type of control condition, and outcome measure.
+However, the small sample size limits our ability to include these moderators in mixed-effects meta-analysis without risking overfitting (modeling random noise in the data, rather than true moderating effects).
+We therefore used metaforest [ @van_lissa_metaforest:_2017] to screen for relevant moderators.
+This technique uses the machine learning algorithm "random forests" to prevent overfitting, and to assess the importance of several potential moderators.
+An added benefit is that metaforest can capture non-linear relationships between moderators and effect size, and higher-order interactions.
+To this end, many (in this case, 10000) bootstrap samples are drawn from the original data, and a models is estimated on each bootstrap sample.
+Then, each model's performance is evaluated on cases not part of its bootstrap sample, yielding an estimate of explained variance in new data, $R^2_{oob}$.
+We conducted random-effects weighted metaforest, with clustered bootstrapping to account for the multilevel structure of the data  is negative, this means that the average effect size is a better predictor of out-of-bootstrap cases than the model-implied predictions.
+In other words, the model did not capture generalizable relationships between the moderators and effect size, and we did not find evidence for associations between the moderators and effect size.

### 2021-12-13 manuscript_placebo.Rmd
first analysis

---
title: "Untitled"
output: github_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---
<script src="//yihui.org/js/math-code.js"></script>
<!-- Just one possible MathJax CDN below. You may use others. -->
<script async
  src="//mathjax.rstudio.com/latest/MathJax.js?config=TeX-MML-AM_CHTML">
</script>

```{r setup, include=FALSE}
library("worcs")
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
# load_data()
knitr::opts_chunk$set(echo = TRUE)
run_everything = FALSE
source("../model_accuracy.R")
get_signs <- function(pdps){
  sapply(pdps, function(x){
    thisvar <- x$data
    out <- table(sign(c(-1, 0, 1, diff(thisvar$preds))))-1
    if(any(out[c(1,3)] == 0) & !all(out[c(1,3)] == 0)){
      out <- c(out, c("Negative monotonous", "Positive monotonous")[which(!out[c(1,3)] == 0)])
    } else {
      if(!out[1] == out[3]){
        out <- c(out, c("Mostly negative", "Mostly positive")[(out[1] < out[3])+1])
      } else {
        out <- c(out, "Other")
      }
    }
    dif_amount <- tapply(c(0,0,0, diff(thisvar$preds)), c(-1, 0, 1, sign(diff(thisvar$preds))), sum)
    if(any(dif_amount[c(1,3)] == 0) & !all(dif_amount[c(1,3)] == 0)){
      dif_amount <- c(dif_amount, c("Negative monotonous", "Positive monotonous")[which(!dif_amount[c(1,3)] == 0)])
    } else {
      if(abs(dif_amount[3]+.00001) / abs(dif_amount[1]+.00001) > 3){
        dif_amount <- c(dif_amount, "Mostly positive")
      } else {
        if(abs(dif_amount[1]+.00001) / abs(dif_amount[3]+.00001) > 3){
          dif_amount <- c(dif_amount, "Mostly negative")
        } else {
          if(!((abs(dif_amount[3]+.00001) / abs(dif_amount[1]+.00001) > 3) | (abs(dif_amount[1]+.00001) / abs(dif_amount[3]+.00001) > 3))){
            dif_amount <- c(dif_amount, "Other")
          }
        }
      }
    }
    c(names(thisvar)[1], out, dif_amount)
  })
}

```

## Multicolinearity analysis

```{r, message = FALSE}
library(worcs)
library(readxl)
library(tidySEM)
library(metaforest)
# Email from Xavier:
# The dataset has 2 sheets. In sheet #1 you will find the data to be analysed and in sheet #2 the description of the study variables.
load_data()
dictionary <- read.csv("../dictionary.csv", stringsAsFactors = FALSE)

dictionary <- dictionary[!is.na(dictionary$Meaning), 1:2]
dictionary <- dictionary[-c(6,30), ]

# Patient-related covariates: mean age, gender (% of men), illness severity at baseline, previous treatment (treatment naïve), ethnicity (% Caucasian).
#dictionary[7:10, ]
mod_patient <- c(`Mean age` = "mean_age_1",
                 `Male (p)` = "men_1_imputed",
                 `Severity at baseline` = "mean_adhd1_baseline_t_imputed",
                 `Treatment naïve` = "naive_an_crit_incl",
                 `Ethnicity` = "white_1_imputed")

# Intervention related covariates: type of drug, concomitant psychotherapy, legal status of the drug (approved vs non approved (= investigational); approved for ADHD vs non-approved for ADHD)
#dictionary[12:14, ]
mod_intervention <-  c(`Stimulant` = "stimulant_investigated",
                       `Therapy` = "psychother_c",
                       `Approved` = "approved_adhd")

# Study design related covariates: study design (parallel vs cross-over), number of sites (or number of patients per study site or sample size), drug dosage (fixed versus variable), RCT duration, number of study arms, comorbidity as an inclusion criterion, proportion of patients assigned to placebo/probability of receiving placebo, duration of wash-out, % dropouts in the placebo arm, type of analysis (ITT: Yes/No).
#dictionary[16:23, ]
mod_design <- c(`Study design` = "parall_dis",
                `Sites` = "num_centers_imputed",
                `Drug dosage` = "fixed_dosification_imputed",
                `RCT duration` = "length_treat2",
                `Placebo (p)` = "prob_pbo",
                `Comorbidity` = "comorb_incl_crit",
                `ITT analysis` = "itt_analyisis"
)

# Other: Publication year, region (USA/others), sponsorship.
# Risk of bias: High risk of bias using the Cochrane risk of bias tool (Yes/No).
#dictionary[16:23, ]
#data$year <- as.numeric(format(data$publication_date, format = "%Y"))
data$year <- as.numeric(substring(data$publication_date, 1, 4))
mod_other <- c(`Year` = "year",
               `USA` = "usa",
               `Sponsorship` = "pharm_ind_main",
               `Risk of bias` = "high_rob")

mods <- c(mod_patient,
          mod_intervention,
          mod_design,
          mod_other
)

# Code factors
desc <- descriptives(data)
is_factor <- desc$unique == 2 & sapply(data, function(x){all(x %in% c(0,1))})
data[is_factor] <- lapply(data[is_factor], factor)

# Covariates with more than 50% of missing data will be removed.

# According to the protocol, now you should:
#   1.	examine multicollinearity, using the generalized VIF (https://github.com/cjvanlissa/metafor/blob/master/R/vif.rma.r).

dat <- escalc(measure = "MN", mi = data$mean_adhd1_change_1, sdi = data$sd_adhd1_change_1_imputed, ni = data$n_adhd1_change_1, data = data[mods])

res <- rma(yi = dat$yi,
           vi = dat$vi,
           mods = model.matrix(~., data[mods])[,-1])
vifs <- vif(res)
write.csv(vifs, "vif.csv")
worcs:::write_gitig(".gitignore", "!vif.csv")

# Please, let us know what are the findings of this analysis. If no collinearity is found, the next steps will be splitting the sample in two and carrygin out the metaregression/metaforest analyses using the training data set.
```

We examined multicolinearity by running a random effects meta-analysis with all predictors included, and computing the generalized VIF. Values ranged from $[`r report(min(vifs), equals = F)`, `r report(max(vifs), equals = F)`]$, thus indicating no evidence of multicolinearity.

## Split training/testing sample

Subsequently, we split the data into a training and testing sample, using the preregistered seed value.

```{r}
set.seed(4286)
train <- sample(unique(data$id), size = .7*length(unique(data$id)), replace = FALSE)
yaml::write_yaml(train, "split.yml")
train <- yaml::read_yaml("split.yml")
df_train <- dat[data$id %in% train, ]
df_test <- dat[!data$id %in% train, ]
```

The training data had `r nrow(df_train)` cases, and the testing data had `r nrow(df_test)` cases.

## Metaforest model

To build a metaforest model, we first conducted an analysis with random effects weights and default settings, with 20000 iterations to determine the number of trees required to reach convergence.

```{r}
# Run model with many trees to check convergence
set.seed(6473)
check_conv <- MetaForest(yi~.,
                        data = df_train,
                        whichweights = "random",
                        num.trees = 20000)
# Plot convergence trajectory
```

```{r figconverge, echo=FALSE, fig.cap="Convergence plot"}
# Plot convergence trajectory
plot(check_conv)
```

It can be seen that this model has converged within approximately 10000 trees (Figure \@ref(fig:figconverge)). Thus, we will use this number of trees for subsequent analyses.

```{r, echo = FALSE}
# Run recursive preselection, store results in object 'preselect'
set.seed(73829)
mf_rep <- MetaForest(yi~.,
                        data = df_train,
                        whichweights = "random",
                        num.trees = 10000)
preselected <- preselect(mf_rep,
                         replications = 100
                         )
# Plot the results
plot(preselected)
# Retain only moderators with positive variable importance in more than
# 50% of replications
retain_mods <- preselect_vars(preselected, cutoff = .95)

```

Next, we tune the model using the R-package \texttt{caret}, which offers a uniform workflow for any machine learning task. The function \texttt{ModelInfo_mf} tells caret how to tune a MetaForest analysis. As tuning parameters, we consider all three types of weights (uniform, fixed-, and random-effects), number of candidate variables at each split from 2-6, and a minimum node size from 2-6. We select the model with smallest prediction error (RMSE) as final model, based on 10-fold clustered cross-validation. Clustered cross-validation means that effect sizes from the same study are always included in the same fold, to account for the dependency in the data. Note that the number of folds cannot exceed the number of clusters in the data. Moreover, if the number of clusters is very small, one might have to resort to specifying the same number of folds as clusters. Model tuning typically takes a long time; for this small dataset, it might take five minutes; for a very large dataset, it might take hours. However, when your dataset is larger, you will often reach model convergence at a lower number of trees, which reduces computation time.

```{r}
# Load the caret library
if(run_everything){
  library(caret)
# Set up 10-fold CV
cv_folds <- trainControl(method = "cv", 
                           index = createFolds(df_train$yi))

# Set up a tuning grid for the three tuning parameters of MetaForest
tuning_grid <- expand.grid(whichweights = c("random", "fixed", "unif"),
                       mtry = 2:6,
                       min.node.size = 2:6)

# X should contain only retained moderators, clustering variable, and vi
X <- df_train[, c("vi", retain_mods)]

# Train the model
mf_cv <- train(y = df_train$yi,
               x = X,
               method = ModelInfo_mf(), 
               trControl = cv_folds,
               tuneGrid = tuning_grid,
               num.trees = 10000)
  saveRDS(mf_cv, "mf_cv.RData")
}

mf_cv <- readRDS("mf_cv.RData")
best <- metaforest:::best(mf_cv)
# Extract R^2_{cv} for the optimal tuning parameters
r2_cv <- mf_cv$results$Rsquared[which.min(mf_cv$results$RMSE)]

```

Based on the root mean squared error, the best combination of tuning parameters were `r best[1]` weights, with `r best[2]` candidate variables per split, and a minimum of `r best[3]` cases per terminal node. We examined convergence of the final model (Figure \@ref(fig:figconvergetuned)). Then, we examine the $R^2_{oob}$.

```{r}
# For convenience, extract final model
final <- mf_cv$finalModel
# Extract R^2_{oob} from the final model
r2_oob <- final$forest$r.squared
# Examine performance on testing set
test_performance <- model_accuracy(final, 
                                   newdata = data.frame(.outcome = df_test$yi, df_test[mods]),
                                   observed = df_test$yi,
                                   ymean = mean(df_train$yi))
```

```{r figconvergetuned, echo=FALSE, fig.cap="Convergence plot for final model"}
# Plot convergence
plot(final)
```

```{r figvarimp, fig.cap="Variable importance plot"}
# Plot variable importance
VarImpPlot(final)
```

```{r figpd, fig.cap="Marginal relationship of moderators with effect size"}
ordered_vars <- names(final$forest$variable.importance)[
  order(final$forest$variable.importance, decreasing = TRUE)]
# Plot partial dependence
PartialDependence(final, vars = ordered_vars,
                  rawdata = TRUE, pi = .95)
```

We can conclude that the model has converged, and has a positive estimate of explained variance in new data, $R^2_{oob} = `r formatC(r2_oob, digits = 2, format = "f")`$, $R^2_{cv} = `r formatC(r2_cv, digits = 2, format = "f")`$. However, the model has negative explained variance in the testing data, $R^2_{test} = `r formatC(test_performance["r2"], digits = 2, format = "f")`$. Thus, the model appears to be overfit. We will plot the variable importance (Figure \@ref(fig:figvarimp)), and partial dependence plots (Figure \@ref(fig:figpd)).

```{r}
if(run_everything){
  set.seed(34)
  p <- PartialDependence(x = final, vars = ordered_vars, output = "list", rawdata = TRUE)
  saveRDS(p, "p_train.RData")
  #source("../get_signs.R")

}
p <- readRDS("p_train.RData")
the_signs <- t(get_signs(p))
# Number variables
p <- lapply(1:length(p), function(i){
  p[[i]]+facet_grid(.~Variable, labeller = labeller(
    Variable = setNames(paste0(i, ". ", ordered_vars[i]), ordered_vars[i])
  ))
})

# Reduce font size
p <- lapply(p, function(x){ x + theme(strip.text.x = element_text(size = 6),
                                      axis.text.x = element_text(size = 6),
                                      axis.text.y = element_text(size = 6))})

p_pdp <- metaforest:::merge_plots(p)
ggsave(
  filename = "rf_pdp_numbered.png",
  p_pdp,
  device = "png")
svg("rf_pdp_numbered.svg")
eval(p_pdp)
dev.off()

dirs <- data.frame(the_signs)
VI <- sort(final$forest$variable.importance, decreasing = TRUE)
VI <- data.frame(Variable = paste0(1:length(VI), ". ", names(VI)), Importance = VI, Direction = dirs$V9[match(names(VI), dirs$V1)])
VI$Variable <- ordered(VI$Variable, levels = rev(VI$Variable))
VI$Direction <- ordered(VI$Direction, levels = c("Positive monotonous", "Mostly positive", "Other", "Mostly negative", "Negative monotonous"))

p_vi <- ggplot(VI, aes_string(y = "Variable", x = "Importance")) + 
  geom_segment(aes_string(x = 0, xend = "Importance", 
                          y = "Variable", yend = "Variable"), colour = "grey50", 
               linetype = 2) +
  geom_vline(xintercept = 0, colour = "grey50", 
             linetype = 1) +
  xlab("Permutation Importance") + 
  theme_bw() + theme(panel.grid.major.x = element_blank(), 
                     panel.grid.minor.x = element_blank(),
                     axis.title.y = element_blank(),
                     axis.text.y = element_text(hjust=0)) + 
  geom_point(aes_string(fill = "Direction"), shape = 21, size = 2) + 
  scale_fill_grey(start = 1, end =0) +
  #scale_fill_manual(values = c("Mostly positive" = "white", "Mostly negative" = "gray80", "Negative" = "black", "Other" = "gray50")) + 
  theme(legend.position = c(0.8, 0.2))
ggsave(
  filename = "varimp.png",
  p_vi,
  device = "png")
svg("varimp.svg")
eval(p_vi)
dev.off()

imp_p <- ranger::importance_pvalues(final$forest, formula = .outcome ~., data = final$data, method = "altmann")
VI$pvalue <- imp_p[,2][match(rownames(VI), rownames(imp_p))]
write.csv(VI, "table4.csv", row.names = FALSE)
metaforest:::predict.MetaForest()
df <- as.data.frame(data[data$id %in% tmp, match(names(final$data)[-1], names(data))])
pred <- predict(final, data = df)
write.table(pred$predictions, "clipboard", sep = "\n")
```

The definitive analysis was performed by applying to the whole data set the method that was found the most accurate, in this case MetaForest.

```{r}
set.seed(684842)
mf_full <- MetaForest(as.formula(paste0("yi~", paste0(ordered_vars, collapse = " + "))),
                      data = dat,
                      whichweights = "unif",
                      mtry = 3,
                      min.node.size = 2,
                      num.trees = 10000)

if(run_everything){
  set.seed(34)
  p <- PartialDependence(x = mf_full, vars = ordered_vars, output = "list", rawdata = TRUE)
  saveRDS(p, "p_full.RData")
}
p <- readRDS("p_full.RData")

the_signs <- t(get_signs(p))
# Number variables
p <- lapply(1:length(p), function(i){
  p[[i]]+facet_grid(.~Variable, labeller = labeller(
    Variable = setNames(paste0(i, ". ", ordered_vars[i]), ordered_vars[i])
  ))
})

# Reduce font size
p <- lapply(p, function(x){ x + theme(strip.text.x = element_text(size = 6),
                                      axis.text.x = element_text(size = 6),
                                      axis.text.y = element_text(size = 6))})

p_pdp <- metaforest:::merge_plots(p)
ggsave(
  filename = "rf_pdp_numbered_fulldata.png",
  p_pdp,
  device = "png")
svg("rf_pdp_numbered_fulldata.svg")
eval(p_pdp)
dev.off()

dirs <- data.frame(the_signs)
VI <- sort(mf_full$forest$variable.importance, decreasing = TRUE)
VI <- data.frame(Variable = paste0(1:length(VI), ". ", names(VI)), Importance = VI, Direction = dirs$V9[match(names(VI), dirs$V1)])
VI$Variable <- ordered(VI$Variable, levels = rev(VI$Variable))
VI$Direction <- ordered(VI$Direction, levels = c("Positive monotonous", "Mostly positive", "Other", "Mostly negative", "Negative monotonous"))

p_vi <- ggplot(VI, aes_string(y = "Variable", x = "Importance")) + 
  geom_segment(aes_string(x = 0, xend = "Importance", 
                          y = "Variable", yend = "Variable"), colour = "grey50", 
               linetype = 2) +
  geom_vline(xintercept = 0, colour = "grey50", 
             linetype = 1) +
  xlab("Permutation Importance") + 
  theme_bw() + theme(panel.grid.major.x = element_blank(), 
                     panel.grid.minor.x = element_blank(),
                     axis.title.y = element_blank(),
                     axis.text.y = element_text(hjust=0)) + 
  geom_point(aes_string(fill = "Direction"), shape = 21, size = 2) + 
  scale_fill_grey(start = 1, end =0) +
  #scale_fill_manual(values = c("Mostly positive" = "white", "Mostly negative" = "gray80", "Negative" = "black", "Other" = "gray50")) + 
  theme(legend.position = c(0.8, 0.2))
ggsave(
  filename = "varimp_fulldata.png",
  p_vi,
  device = "png")
svg("varimp_fulldata.svg")
eval(p_vi)
dev.off()

imp_p <- ranger::importance_pvalues(mf_full$forest, formula = yi ~., data = mf_full$data, method = "altmann")
VI$pvalue <- imp_p[,2][match(rownames(VI), rownames(imp_p))]
write.csv(VI, "table4_fulldata.csv", row.names = FALSE)
```

### 2021-12-13 prepare_data.R

@@ -9,32 +9,15 @@ library(tidySEM)
 dat <- readxl::excel_sheets("SR_SSRI_FearLearning_ForestPlot_data_20211018_Caspar.xlsx")
 dat <- lapply(dat[-1], function(x){
   tmp <- as.data.frame(readxl::read_xlsx(path = "SR_SSRI_FearLearning_ForestPlot_data_20211018_Caspar.xlsx", sheet = x))
+  tmp[["Remarks"]] <- NULL
   names(tmp) <- tolower(names(tmp))
-  tmp[["remarks"]] <- NULL
+  numers <- tolower(c("Mean experimental group", "SD experimental group",
+              "Number of animals in intervention group", "Mean control group",
+              "SD control group", "Number of animals in control group"))
+  cats <- names(tmp)[!names(tmp) %in% numers]
+  tmp[numers] <- lapply(tmp[numers], as.numeric)
   tmp$Process = x
   tmp
 })
 dat <- tidySEM:::bind_list(dat)
 open_data(dat)
-#   Information regarding this data file for the SR fear learning & SSRIs
-#
-# This data file is organised by fear learning process. This means that every fear learning process has its own Excel sheet.
-#
-# Within these sheets you find the same layout. The different columns are explained below:
-#
-#   Study name
-# Article code
-# Type of SSRI
-# Frequency
-# Disease induction
-# Species
-# Type of test
-# Sensitivity analysis
-#
-#
-#
-# Analyses we want to perform:
-#
-#   1. Separate meta-analyses of the five fear learning processes that have enough data (acq learn to cue, acq learn to ctx, acq retr to cue, acq retr to ctx, ext learn to cue)
-# 2. Subgroup analyses of the five factors (SSRI, frequency, disease induction, species, type of test) per fear learning process
-# 3. Check for multi collinearity

### 2021-12-14 manuscript/manuscript.Rmd
final results

@@
 library("worcs")
-library(metafor)
 library(ggplot2)
 library(kableExtra)
+library(DT)
 library(tidySEM)
+library(knitr)
+knitr::opts_chunk$set(echo = FALSE)
+```
+
+```{r prepdata, eval=run_everything}
+library(metafor)
+library(pema)
+
 # We recommend that you prepare your raw data for analysis in 'prepare_data.R',
@@
 # dat[c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group", "mean.control.group", "mean.experimental.group", "sd.control.group", "sd.experimental.group")] <- NULL
+
+# Rename
+rnm <- read.csv("../rename.csv", stringsAsFactors = F, encoding = "UTF-8")
+names(rnm) <- c("orig", "Rename")
+mods <- c("type.of.ssri", "frequency", "disease.induction", "species", 
+"type.of.test")
+for(v in mods){
+  these <- rnm[grepl(v, rnm$orig),]
+  orig_levs <- gsub(v, "", these$orig)
+  nulev <- gsub("^.+?\\.", "", these$Rename)
+  levels(dat[[v]]) <- nulev[match(orig_levs, levels(dat[[v]]))]
+}
+
+names(dat)[match(mods, names(dat))] <- c("ssri", "freq", "disease", "species", "test")
 dat <- dat[!is.na(dat$yi), ]
@@
 dat$id_es <- 1:nrow(dat)
-knitr::opts_chunk$set(echo = TRUE)
+saveRDS(dat, "dat.RData")
+```
+
+```{r}
+dat <- readRDS("dat.RData")
+processes <- levels(dat$Process)
+mods <- c("ssri", "freq", "disease", "species", "test")
 ```
@@
                         y = c(max(df_es$y)+2, max(df_es$y)+2.5, max(df_es$y)+2, max(df_es$y)+1.5))
-
+ylabsize = 10
+if(p == "Acq retr to ctx") ylabsize =1
 pforest <- ggplot(data=df_es)+ 
@@
   geom_hline(yintercept=max(df_es$y)+1)+
+  theme(axis.text.y = element_text(size=ylabsize))+
   theme_minimal()
@@
 ggsave(paste0("threelevel_ma_forest", p, ".png"), pforest, device = "png")
+if(p == "Acq retr to ctx") ggsave(paste0("threelevel_ma_forest", p, ".png"), pforest, device = "png", width = 7, height = 12)
 res = data.frame(Variance = c("Overall ES", "V within", "V between"),
@@
 saveRDS(mlm, "mlm.RData")
+
+tb <- lapply(1:length(processes), function(i){
+  tb <- mlm[[i]]$res
+  tb$Process <- processes[i]
+  tb
+})
+tb <- do.call(rbind, tb)
+tb$CI <- tidySEM::conf_int(lb = tb$ci.lb, ub = tb$ci.ub)
+tb[c("ci.lb", "ci.ub")] <- NULL
+names(tb) <- c("Parameter", "Estimate", "p", "Process", "CI")
+write.csv(tb, "tab_threelevel.csv", row.names = FALSE)
 ```
@@
 
-The effect size estimates ranged from `r formatC(min(dat[["yi"]]), digits = 2, format = "f")` to `r formatC(max(dat[["yi"]]), digits = 2, format = "f")` ($M = `r report(mean(dat[["yi"]]))`, SD = `r report(sd(dat[["yi"]]))`$).
-One study had an effect size estimate more than standard deviations from the mean effect size ($Z = `r max(zscores)`$); it was removed as an outlier.
+The effect size estimates ranged from `r formatC(min(dat[["yi"]]), digits = 2, format = "f")` to `r formatC(max(dat[["yi"]]), digits = 2, format = "f")` ($M `r report(mean(dat[["yi"]]))`, SD `r report(sd(dat[["yi"]]))`$).
+One study had an effect size estimate almost 15 standard deviations from the mean effect size ($Z = 14.98$); it was removed as an outlier.
 Sample sizes ranged from `r min(rowSums(dat[, c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group")]))` to `r max(rowSums(dat[, c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group")]))` animals ($M = `r formatC(mean(rowSums(dat[, c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group")])), digits = 2, format = "f")`, SD = `r formatC(sd(rowSums(dat[, c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group")])), digits = 2, format = "f")`$).
@@
 
-Meta-analysis was conducted in R [@r_core_team_r:_2017-1] using the R-packages `metafor` [@viechtbauer_conducting_2010-1], and `pema` [@van_lissa_metaforest:_2017-1], following the recommendations of Field and Gillett (2010).
-
-## Three-level meta-analysis
-
-First, we used three-level meta-analysis to account for dependent effect sizes within studies [@van_den_noortgate_meta-analysis_2015].
+Meta-analysis was conducted in R [@rcore] using the R-packages `metafor` [@viechtbauerConductingMetaanalysesMetafor2010], and `pema` [@refpema].
+To estimate overall effects, we used three-level meta-analysis to account for dependent effect sizes within studies [@vandennoortgateMetaanalysisMultipleOutcomes2015].
 Let $y_{jk}$ denote the $j$ observed effect sizes $y$, originating from $k$ studies.
@@
 mlm <- readRDS("mlm.RData")
-tb <- lapply(1:length(processes), function(i){
-  tb <- mlm[[i]]$res
-  tb$Process <- processes[i]
-  tb
-})
-tb <- do.call(rbind, tb)
-tb$CI <- tidySEM::conf_int(lb = tb$ci.lb, ub = tb$ci.ub)
-tb[c("ci.lb", "ci.ub")] <- NULL
-names(tb) <- c("Parameter", "Estimate", "p", "Process", "CI")
-kbl(tb[, c("Parameter", "Estimate", "CI", "p", "Process")], digits = 2)
+tb <- read.csv("tab_threelevel.csv", stringsAsFactors = FALSE)
+# kbl(tb[, c("Parameter", "Estimate", "CI", "p", "Process")], digits = 2) |>
+#   kable_styling(bootstrap_options = c("striped", "hover"))
+datatable(tb, rownames= FALSE, options = list(
+              "pageLength" = nrow(tb))) |>
+  formatRound(columns=c('Estimate', 'p'), digits=2)
 ```
@@
 
+## Forest plots
+
+The forest plots for the aforementioned three-level meta-analyses are presented below.
+Within each plot, studies are ranked by their sampling variance $vi$;
+thus, the most precise estimates are at the bottom, near the overall effect.
+
+```{r runplots, include=FALSE}
+out = NULL
+for (i in 1:length(processes)) {
+  out = c(out, knit_expand('forest.rmd'))
+}
+```
+
+`r paste(knit(text = out), collapse = '\n')`
+
 ## Moderator analyses
 
-Five moderators were coded: (SSRI, frequency, disease induction, species, type of test).
+Five categorical moderators were coded: (SSRI, frequency, disease induction, species, type of test).
 The effect of these moderators was investigated using meta-regression.
+Note however that 77 dummy variables were required to encode all conditions of these categorical moderators.
+As this exceeded in many cases the number of available effect sizes (per process),
+these models were not identified.
+Addressing this problem requires performing variable selection.
+Three steps were taken to do so. 
+First, categories that did not occur within one subset of the data (by process) were omitted, as their dummy variables are constant for that specific dataset.
+Secondly, some dummy variables were redundant because some studies had identical values on multiple dummy variables.
+Only one of these redundant dummy variables was retained, and its name was updated to reflect all redundant dummies it represents.
+Thirdly, despite these measures, many meta-regression models dropped all or some of the predictors, suggesting the models were empirically non-identified.
+Although these models are available in the online supplemental materials,
+we advise against their substantive interpretation.
+
+The problems with meta-regression suggests that a technique is required that performs variable selection during analysis.
+Such a technique was recently developed: Bayesian penalized meta-regression (BRMA), as implemented in the `pema` R-package (@refpema).
+By imposing a regularizing (horseshoe) prior on the regression coefficients,
+BRMA shrinks all coefficients towards zero, which aids empirical model identification.
+Coefficients must overwhelm the prior in order to become significantly different from zero.
+Thus, this method also performs variable selection: identifying which moderators are important in predicting the effect size.
+The resulting regression coefficients are negatively biased by design, but the estimate of residual heterogeneity $\tau^2$ is unbiased.
+Note that, as this is a Bayesian model, inference is based on credible intervals.
+A credible interval is interpreted as follows: The population value falls within this interval with 95% probability (certainty).
+This is different from the interpretation of frequentist confidence intervals, which are interpreted as follows: In the long run, 95% of confidence intervals contain the population value.
+
 Because the within-studies variance component was non-significant in most three-level analyses,
@@
 
-```{r}
-mods <- c("type.of.ssri", 
-"frequency", "disease.induction", "species", "type.of.test")
-# 
-# mlm <- lapply(processes, function(p){
-#   df <- dat[dat$Process == p, ]
-#   modmat <- model.matrix(~., df[mods])[,-1]
-#   zerocols <- colSums(modmat) == 0
-#   zero <- colnames(modmat)[zerocols]
-#   modmat <- modmat[, !zerocols]
-#   dupcols <- which(duplicated(as.list(data.frame(modmat))))
-#   dups <- colnames(modmat)[dupcols]
-#   modmat <- modmat[, !dupcols]
-# res <- rma(yi = df$yi,
-#            vi = df$vi,
-#            mods = modmat)
-#vifs <- vif(res)
-#})
-# res <- rma(yi = dat$yi,
-#            vi = dat$vi,
-#            mods = model.matrix(~., data[mods])[,-1])
-# vifs <- vif(res)
+```{r, eval = run_everything}
+library(metacart)
+modres <- lapply(processes, function(p){
+  df <- dat[dat$Process == p, ]
+  modmat <- model.matrix(~., df[mods])[,-1]
+  constcols <- colSums(modmat) == 0 | colSums(modmat) == nrow(modmat)
+  constcolnames <- colnames(modmat)[constcols]
+  modmat <- modmat[, !constcols]
+  modmatlist <- as.list(data.frame(modmat))
+  dupcols <- duplicated(modmatlist)
+  modmat <- modmat[, !dupcols]
+  these_dups <- modmatlist[dupcols]
+  modmatlist <- as.list(data.frame(modmat))
+  for(i in 1:length(these_dups)){
+    idnum <- which(duplicated(c(modmatlist, these_dups[i]), fromLast = T))
+    colnames(modmat)[idnum] <- paste0(colnames(modmat)[idnum], ";", names(these_dups)[i])
+  }
+  res <- rma(yi = df$yi,
+             vi = df$vi,
+             mods = modmat)
+  vifs <- vif(res)
+  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2"),
+                       cbind(
+                         Estimate = c(res$b, res$tau2),
+                         se = c(res$se, res$se.tau2),
+                         ci.lb = c(res$ci.lb, res$tau2-1.96*res$se.tau2),
+                         ci.ub = c(res$ci.ub, res$tau2+1.96*res$se.tau2),
+                         p = c(res$pval, res$QEp)))
+  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
+  tabres[c("ci.lb", "ci.ub")] <- NULL
+  tabres$VIF <- c(NA, vifs$vif, NA)
+  write.csv(tabres, paste0("rma_mods_", p, ".csv"))
 
-# write.csv(vifs, "vif.csv")
-# worcs:::write_gitig(".gitignore", "!vif.csv")
+  moddat <- data.frame(df[c("yi", "vi")], modmat)
+  pma <- brma(yi ~., data = moddat)
+  sumpma <- data.frame(summary(pma)$coefficients)
+  sumpma <- cbind(rownames(sumpma), sumpma)
+  names(sumpma)[1:3] <- c("Parameter", "Estimate", "se")
+  sumpma <- sumpma[!sumpma$Parameter == "tau", ]
+  rownames(sumpma) <- NULL
+  sumpma$CI <- conf_int(lb = sumpma$X2.5., ub = sumpma$X97.5.)
+  pstars <- c("*", "")[as.integer(apply(sumpma[, c("X2.5.", 
+                                                   "X97.5.")], 1, function(x) {
+                                                     sum(sign(x)) == 0
+                                                   })) + 1]
+  sumpma$p <- pstars
+  sumpma[c("sd", grep("^X", names(sumpma), value = T))] <- NULL
+  write.csv(sumpma, paste0("brma_mods_", p, ".csv"))
+  moddatvi <- moddat$vi
+  moddat <- moddat[, -which(colnames(moddat) == "vi")]
+  resmc <- suppressWarnings(metacart::FEmrt(yi~., data = moddat, vi = moddatvi))
+  list(rma = tabres,
+       brma = sumpma,
+       mc = resmc)
+})
+saveRDS(modres, "modres.RData")
+
 ```
 
-<!-- 3. Check for multi collinearity -->
+### Classic meta-regression
 
-```{r results="asis", eval = FALSE}
-apa_table(
-aov_table, caption = "Model fit and likelihood ratio tests", note = "Significance of variance components is assessed by constraining them to zero, and examining the significance of a log-likelihood (ll) ratio test (LRT) comparing the constrained model to the full three-level model.
-", placement = "p"
+```{r}
+modres <- readRDS("modres.RData")
+```
+
+Note that analyses containing VIF values greater than 5 should be regarded as problematic, due to multicolinearity.
+This applies to nearly all models.
+
+```{r, results = "asis", eval = FALSE}
+
+htmltools::tagList(
+  lapply(1:length(processes), function(i) {
+    p <- processes[i]
+    tb <- modres[[i]]$rma
+    tb$format <- as.integer(tb$p < .05)
+    formatStyle(
+      formatRound(
+        datatable(
+          tb,
+          rownames = FALSE,
+          caption = paste0("Meta-regression coefficients for ", p),
+          options = list(columnDefs = list(list(
+            targets = 6, visible = FALSE
+          )),
+          "pageLength" = nrow(tb))
+        ),
+        columns = c('Estimate', "se", 'p', "VIF"),
+        digits = 2
+      ),
+      "format",
+      target = "row",
+      backgroundColor = styleEqual(c(0, 1), c('gray', 'white'))
+    )
+  })
 )
 
-failsafe <- fsn(d, vi, data = data)
 ```
 
-*A chi-square test of homogeneity of effect sizes was not significant, 2(19) 21.53, p=.37. These measures suggest considerable similarity in effect sizes across studies.*
-*Consistent with this finding, moderator analysis suggested that the effect of age or sex on the overall effect size was not significant.*
+```{r run-numeric-md, include=FALSE}
+out = NULL
+for (i in 1:length(processes)) {
+  out = c(out, knit_expand('tab_rma_template.rmd'))
+}
+```
 
-```{r funnel_plot, echo=FALSE, warning=FALSE, message=FALSE, results="hide", eval = F}
-png(file="funnel_plot.png",width=148, height=105, units="mm", res = 300)
-funnel(model.full, main=NULL, 
-       back="white", shade="white", hlines="white", xlab = "Effect size (Cohen's d)")
-dev.off()
-cairo_pdf("funnel_plot.pdf", family="Helvetica", width = 5.8, height = 4.1)
-  funnel.rma(model.full, main=NULL, 
-       back="white", shade="white", hlines="white", xlab = "Effect size (Cohen's d)", digits = 2)
-dev.off()
-embed_fonts("funnel_plot.pdf", outfile="funnel_plot.pdf")
-beggstest <- regtest(data$d, data$vi)
-sd(data$age)
+`r paste(knit(text = out), collapse = '\n')`
+
+### Bayesian regularized meta-regression:
+
+```{r, results = "asis", eval = FALSE}
+for(i in 1:length(processes)){
+  p <- processes[i]
+  tb <- modres[[i]]$brma
+  tb$format <- as.integer(tb$p == "*")
+  print({datatable(tb, rownames= FALSE, caption = paste0("Bayesian regularized meta-regression coefficients for ", p), options = list(
+              "pageLength" = nrow(tb))) |>
+  formatRound(columns=c('Estimate', 'p'), digits=2)})
+}
+htmltools::tagList(
+  lapply(1:length(processes), function(i) {
+    p <- processes[i]
+    tb <- modres[[i]]$brma
+    tb$format <- as.integer(tb$p < .05)
+    formatStyle(
+      formatRound(
+        datatable(
+          tb,
+          rownames = FALSE,
+          caption = paste0("Bayesian regularized meta-regression coefficients for ", p),
+          options = list(columnDefs = list(list(
+            targets = 7, visible = FALSE
+          )),
+          "pageLength" = nrow(tb))
+        ),
+        columns = c('Estimate', "se"),
+        digits = 2
+      ),
+      "format",
+      target = "row",
+      backgroundColor = styleEqual(c(0, 1), c('gray', 'white'))
+    )
+  })
+)
+
 ```
-File drawer analysis [@rosenthal_file_1979] revealed that `failsafe[["fsnum"]]` unpublished, filed, or unretrieved studies averaging null results would be required to bring the average unweighted effect size to nonsignificance.
-Visual inspection of the Funnel plot (Figure 3) did not clearly indicate asymmetry, which could be a sign of publication bias.
-Begg's test of funnel asymmetry (based on random-effects meta-analysis) similarly did not indicate significant bias, $Z = ` formatC(beggstest[["zval"]], digits = 2, format = "f")`$, $p = `formatC(beggstest[["pval"]], digits = 2, format = "f")`$.
 
-## Moderation
+```{r run-numeric-md2, include=FALSE}
+out = NULL
+for (i in 1:length(processes)) {
+  out = c(out, knit_expand('tab_brma_template.rmd'))
+}
+```
 
-We coded several potential theoretical and methodological moderators: Proportion of male participants, average age of the sample, type of population (typical or socially anxious), type of intervention, type of control condition, and outcome measure.
-However, the small sample size limits our ability to include these moderators in mixed-effects meta-analysis without risking overfitting (modeling random noise in the data, rather than true moderating effects).
-We therefore used metaforest [ @van_lissa_metaforest:_2017] to screen for relevant moderators.
-This technique uses the machine learning algorithm "random forests" to prevent overfitting, and to assess the importance of several potential moderators.
-An added benefit is that metaforest can capture non-linear relationships between moderators and effect size, and higher-order interactions.
-To this end, many (in this case, 10000) bootstrap samples are drawn from the original data, and a models is estimated on each bootstrap sample.
-Then, each model's performance is evaluated on cases not part of its bootstrap sample, yielding an estimate of explained variance in new data, $R^2_{oob}$.
-We conducted random-effects weighted metaforest, with clustered bootstrapping to account for the multilevel structure of the data  is negative, this means that the average effect size is a better predictor of out-of-bootstrap cases than the model-implied predictions.
-In other words, the model did not capture generalizable relationships between the moderators and effect size, and we did not find evidence for associations between the moderators and effect size.
+`r paste(knit(text = out), collapse = '\n')`
+
+# Conclusion
+
+Based on three-level multilevel meta-analyses,
+there is limited evidence that overall effects are non-zero in the population,
+except for the processes "Acq retr to ctx" and "Ext retr to ctx".
+All processes showed significant between-studies variance, except "Ext retr to cue".
+Conversely, none of the processes showed significant within-studies variance, except "Acq retr to ctx".
+There is thus substantial evidence that heterogeneity in effect sizes is mostly due to between-studies differences.
+
+Classic meta-regression analyses were largely invalid for moderator analysis,
+because of high multicolinearity among predictors.
+BRMA analyses were used, which are robust to multicolinearity, and perform variable selection by shrinking regression coefficients towards zero.
+These BRMA analyses revealed no consistent evidence of any significant moderator effect across processes.
+To exclude the possibility that multiple dummies interacted together,
+I conducted additional sensitivity analyses using `metaCART` - a decision-tree based algorithm that inherently accommodates interactions between dummies.
+However, the `metaCART` analyses also did not find evidence of interaction effects.

### 2021-12-14 manuscript/tab_rma_template.Rmd
final results

```{r tabrma{{i}}, results = 'asis'}
p <- processes[{{i}}]
    tb <- modres[[{{i}}]]$rma
    tb$format <- as.integer(tb$p < .05)
    formatStyle(
      formatRound(
        datatable(
          tb,
          rownames = FALSE,
          caption = paste0("Meta-regression coefficients for ", p),
          options = list(columnDefs = list(list(
            targets = 6, visible = FALSE
          )),
          "pageLength" = nrow(tb))
        ),
        columns = c('Estimate', "se", 'p', "VIF"),
        digits = 2
      ),
      "format",
      target = "row",
      backgroundColor = styleEqual(c(0, 1), c('gray', 'white'))
    )
```

### 2021-12-21 manuscript/manuscript.Rmd
update 2021-12-21 18:18:06

--- 2021-12-13 manuscript/manuscript.Rmd
@@
 ---
-title: "Untitled"
-output: github_document
+title: "Meta-analysis fear learning"
+author: "Caspar J. Van Lissa, for Elise Heesbeen & Lucianne Groenink"
+output: bookdown::html_document2
 date: '`r format(Sys.time(), "%d %B, %Y")`'
@@
 ```{r setup, include=FALSE}
+run_everything = FALSE
 library("worcs")
+library(ggplot2)
+library(kableExtra)
+library(DT)
+library(tidySEM)
+library(knitr)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+```
+
+```{r prepdata, eval=run_everything}
+library(metafor)
+library(pema)
 # We recommend that you prepare your raw data for analysis in 'prepare_data.R',
@@
 # (whichever is available), to allow anyone to reproduce your code:
-# load_data()
-knitr::opts_chunk$set(echo = TRUE)
+load_data()
+dat$Process <- ordered(dat$Process, levels = unique(dat$Process))
+processes <- levels(dat$Process)
+totaln <- dat[!duplicated(dat$article.code), c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group", "Process")]
+totaln <- sapply(processes, function(p){ sum(totaln[totaln$Process == p, -3], na.rm = TRUE)})
+
+dat <- escalc(measure = "SMD",
+         n1i = dat$number.of.animals.in.control.group,
+         n2i = dat$number.of.animals.in.intervention.group,
+         m1i = dat$mean.control.group,
+         m2i = dat$mean.experimental.group,
+         sd1i = dat$sd.control.group,
+         sd2i = dat$sd.experimental.group,
+         data = dat)
+# dat[c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group", "mean.control.group", "mean.experimental.group", "sd.control.group", "sd.experimental.group")] <- NULL
+
+# Rename
+rnm <- read.csv("../rename.csv", stringsAsFactors = F, encoding = "UTF-8")
+names(rnm) <- c("orig", "Rename")
+mods <- c("type.of.ssri", "frequency", "disease.induction", "species", 
+"type.of.test")
+for(v in mods){
+  these <- rnm[grepl(v, rnm$orig),]
+  orig_levs <- gsub(v, "", these$orig)
+  nulev <- gsub("^.+?\\.", "", these$Rename)
+  levels(dat[[v]]) <- nulev[match(orig_levs, levels(dat[[v]]))]
+}
+
+names(dat)[match(mods, names(dat))] <- c("ssri", "freq", "disease", "species", "test")
+dat <- dat[!is.na(dat$yi), ]
+zscores <- scale(dat[["yi"]])
+maxz <- max(zscores)
+dat <- dat[-which.max(zscores), ]
+# De article code geeft de unieke ID van elk artikel en daarbinnen ook de experimenten aan.
+Bijvoorbeeld: Bijlsma 2015 heeft twee experimenten uitgevoerd en dus zijn er twee effect sizes meegenomen.
+Deze heb ik dan bij het proces ‘acq learn to cue’ aangegeven als Bijlsma 2015 (1) en Bijlsma 2015 (2).
+Nu snap ik ook beter wat jij hiermee bedoelde, sommige artikelen hebben inderdaad meerder effect sizes gerapporteerd maar dat gaat zelfs tot 6 effect sizes bij een aantal artikelen (Leuner 2004 en Ravinder 2013) en niet 4 zoals nu in de tekst staat.
+dat$id_study <- as.integer(dat$article.code)
+dat$id_es <- 1:nrow(dat)
+saveRDS(dat, "dat.RData")
 ```
 
-This manuscript uses the Workflow for Open Reproducible Code in Science [@vanlissaWORCSWorkflowOpen2020] to ensure reproducibility and transparency.
-All code <!--and data--> are available at <git@github.com:cjvanlissa/srma_fearlearning.git>.
-
-This is an example of a non-essential citation [@@vanlissaWORCSWorkflowOpen2020]. If you change the rendering function to `worcs::cite_essential`, it will be removed.
-
-<!--The function below inserts a notification if the manuscript is knit using synthetic data. Make sure to insert it after load_data().-->
-`r notify_synthetic()`
-
-## GitHub Documents
-
-This is an R Markdown format used for publishing markdown documents to GitHub.
-When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
-
-## Including Code
-
-You can include R code in the document as follows:
-
-```{r cars}
-summary(cars)
+```{r}
+dat <- readRDS("dat.RData")
+processes <- levels(dat$Process)
+mods <- c("ssri", "freq", "disease", "species", "test")
 ```
 
-## Including Plots
+<!--   Information regarding this data file for the SR fear learning & SSRIs -->
 
-You can also embed plots, for example:
+<!-- This data file is organised by fear learning process. This means that every fear learning process has its own Excel sheet. -->
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+<!-- Within these sheets you find the same layout. The different columns are explained below: -->
+
+<!--   Study name -->
+<!-- Article code -->
+<!-- Type of SSRI -->
+<!-- Frequency -->
+<!-- Disease induction -->
+<!-- Species -->
+<!-- Type of test -->
+<!-- Sensitivity analysis -->
+
+<!-- Analyses we want to perform: -->
+<!-- 2. Subgroup analyses of the five factors (SSRI, frequency, disease induction, species, type of test) per fear learning process -->
+<!-- 3. Check for multi collinearity -->
+
+```{r threelev, echo=FALSE, warning=FALSE, message=FALSE, results="hide", eval = run_everything}
+mlm <- lapply(processes, function(p){
+  df <- dat[dat$Process == p, ]
+  #Conduct meta-analyses
+  #model.mods <- rma.mv(yi, vi, random = list(~ 1 | id_study, ~ 1 | id_es), data=df) 
+  mod <- rma(df$yi, df$vi) 
+confints <- confint(mod)
+
+tab <- data.frame(Parameter = c(rownames(mod$b), "Tau2"),
+                       cbind(
+                         Estimate = c(mod$b, mod$tau2),
+                         se = c(mod$se, mod$se.tau2),
+                         ci.lb = c(mod$ci.lb, confints$random[1,2]),
+                         ci.ub = c(mod$ci.ub, confints$random[1,3]),
+                         p = c(mod$pval, mod$QEp)))
+  tab$CI <- conf_int(lb = tab$ci.lb, ub = tab$ci.ub)
+  tab[c("ci.lb", "ci.ub")] <- NULL
+  write.csv(tab, paste0("twolevel_ma_", p, ".csv"))
+
+#Write forest plot to file
+xname <- paste0("Hedges' g (", p, ")")
+tmp <- df[order(df$vi, decreasing = TRUE), ]
+df_es <- data.frame(
+    Study = ordered(tmp$article.code, levels = unique(tmp$article.code)),
+    y = 1:nrow(tmp),
+    es = tmp$yi,
+    lb = tmp$yi - 1.96*sqrt(tmp$vi),
+    ub = tmp$yi + 1.96*sqrt(tmp$vi),
+    Process = p)
+
+dfoverall <- data.frame(x = c(mod$ci.ub, mod$b[1,1], mod$ci.lb, mod$b[1,1]),
+                        y = c(max(df_es$y)+2, max(df_es$y)+2.5, max(df_es$y)+2, max(df_es$y)+1.5))
+ylabsize = 10
+if(p == "Acq retr to ctx") ylabsize =1
+pforest <- ggplot(data=df_es)+ 
+  geom_point(aes(y=y, x=es))+ 
+  geom_errorbarh(aes(y = y, xmin=lb, xmax=ub), height=.1)+
+
+  # geom_point(data=data.frame(y = max(df_es$y)+2, es = mod$b[1,1]), aes(y=y, x=es), size=4, shape = 15, fill = "black")+ 
+  # geom_errorbarh(data = data.frame(y = max(df_es$y)+2, lb = mod$ci.lb, ub = mod$ci.ub), aes(y = y, xmin=lb, xmax=ub), height=.4, size = 2)+
+  geom_polygon(data = dfoverall, aes(x = x, y = y))+
+  scale_x_continuous(name=xname, limits = c(min(df_es$lb), min(c(10,max(df_es$ub)))))+
+  scale_y_continuous(name = "", breaks=1:max(df_es$y), labels = df_es$Study, trans="reverse")+
+  #adding a vertical line at the effect = 0 mark
+  geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
+  geom_hline(yintercept=max(df_es$y)+1)+
+  theme(axis.text.y = element_text(size=ylabsize))+
+  theme_minimal()
+
+ggsave(paste0("threelevel_ma_forest", p, ".png"), pforest, device = "png", height = (nrow(df)+2)*.2)
+# if(p == "Acq retr to ctx") ggsave(paste0("threelevel_ma_forest", p, ".png"), pforest, device = "png", 
+#width = 7, height = 12)
+res = data.frame(Variance = c("Overall ES", "Tau2"),
+                 rbind(c(estimate = mod$b[1,1], ci.lb = mod$ci.lb, ci.ub = mod$ci.ub, mod$pval),
+                       c(confints$random[1,], mod$QEp)))
+  list(mod = mod,
+    aov_table = tab,
+       res = res)     
+})
+names(mlm) <- processes
+saveRDS(mlm, "mlm.RData")
+
+tb <- lapply(1:length(processes), function(i){
+  tb <- mlm[[i]]$res
+  tb$Process <- processes[i]
+  tb
+})
+tb <- do.call(rbind, tb)
+tb$CI <- tidySEM::conf_int(lb = tb$ci.lb, ub = tb$ci.ub)
+tb[c("ci.lb", "ci.ub")] <- NULL
+names(tb) <- c("Parameter", "Estimate", "p", "Process", "CI")
+write.csv(tb, "tab_overall.csv", row.names = FALSE)
+```
+```{r, include = FALSE}
+num_effect_sizes <- table(table(dat$article.code))
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+## Descriptive statistics
+
+The effect size estimates ranged from `r formatC(min(dat[["yi"]]), digits = 2, format = "f")` to `r formatC(max(dat[["yi"]]), digits = 2, format = "f")` ($M `r report(mean(dat[["yi"]]))`, SD `r report(sd(dat[["yi"]]))`$).
+One study had an effect size estimate almost 15 standard deviations from the mean effect size ($Z = 14.98$); it was removed as an outlier.
+Sample sizes ranged from `r min(rowSums(dat[, c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group")]))` to `r max(rowSums(dat[, c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group")]))` animals ($M = `r formatC(mean(rowSums(dat[, c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group")])), digits = 2, format = "f")`, SD = `r formatC(sd(rowSums(dat[, c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group")])), digits = 2, format = "f")`$).
+
+## Meta-analysis
+
+Meta-analysis was conducted in R [@rcore] using the R-packages `metafor` [@viechtbauerConductingMetaanalysesMetafor2010], and `pema` [@refpema].
+To estimate overall effects, we used random-effects meta-analysis [@hedgesFixedRandomeffectsModels1998].
+Separate meta-analyses were conducted for each of the fear learning processes.
+The overall pooled effect sizes were:
+
+```{r, results = "asis"}
+mlm <- readRDS("mlm.RData")
+tb <- read.csv("tab_overall.csv", stringsAsFactors = FALSE)
+# kbl(tb[, c("Parameter", "Estimate", "CI", "p", "Process")], digits = 2) |>
+#   kable_styling(bootstrap_options = c("striped", "hover"))
+datatable(tb, rownames= FALSE, options = list(
+              "pageLength" = nrow(tb))) |>
+  formatRound(columns=c('Estimate', 'p'), digits=2)
+```
+
+The overall effect size estimate differed significantly from zero only for `r paste0(tb[tb$Parameter == "Overall ES", ]$Process[tb[tb$Parameter == "Overall ES", ]$p < .05], collapse = ", ")`.
+
+The residual heterogeneity $\tau^2$ was significant for all processes.
+This indicates that there was substantial heterogeneity between effect sizes across studies.
+
+## Forest plots
+
+The forest plots for the aforementioned meta-analyses are presented below.
+Within each plot, studies are ranked by their sampling variance $vi$;
+thus, the most precise estimates are at the bottom, near the overall effect.
+
+```{r runplots, include=FALSE}
+out = NULL
+for (i in 1:length(processes)) {
+  out = c(out, knit_expand('forest.rmd'))
+}
+```
+
+`r paste(knit(text = out), collapse = '\n')`
+
+## Moderator analyses
+
+Five categorical moderators were coded: (SSRI, frequency, disease induction, species, type of test).
+The effect of these moderators was investigated using meta-regression.
+Note however that 33 dummy variables were required to encode all conditions of these categorical moderators.
+As the number of moderators was approximately equal to the number of available effect sizes (per process),
+these models were not identified.
+Addressing this problem requires performing variable selection.
+Three steps were taken to do so.
+First, variables and categories that did not occur within one subset of the data were omitted.
+Secondly, some dummy variables were redundant because some studies had identical values on multiple dummy variables.
+Only one of these redundant dummy variables was retained, and its name was updated to reflect all redundant dummies it represents.
+For example, in the "Acq learn to ctx" sample, all human studies used the Fear potentiated startle test; no other studies used this test. 
+Therefore, these two variables were identical and their effects could not be distinguished.
+Thus, the analysis shows their joint effect as an effect of `specieshuman;testFPS`.
+Thirdly, despite these measures, many meta-regression models dropped all or some of the predictors,
+or failed to converge entirely, suggesting the models were empirically non-identified.
+Although these models are reported below,
+we advise against their substantive interpretation.
+
+The problems with meta-regression can be overcome by a technique that performs variable selection during analysis.
+Such a technique was recently developed: Bayesian penalized meta-regression (BRMA), as implemented in the `pema` R-package (@refpema).
+By imposing a regularizing (horseshoe) prior on the regression coefficients,
+BRMA shrinks all coefficients towards zero, which aids empirical model identification.
+Coefficients must overwhelm the prior in order to become significantly different from zero.
+Thus, this method also performs variable selection: identifying which moderators are important in predicting the effect size.
+The resulting regression coefficients are negatively biased by design, but the estimate of residual heterogeneity $\tau^2$ is unbiased.
+Note that, as this is a Bayesian model, inference is based on credible intervals.
+A credible interval is interpreted as follows: The population value falls within this interval with 95% probability (certainty).
+This is different from the interpretation of frequentist confidence intervals, which are interpreted as follows: In the long run, 95% of confidence intervals contain the population value.
+
+As the models contained only categorical variables but no meaningful reference category,
+we estimated a model _without_ an intercept,
+and instead included an equal number of dummies to the number of unique categories (ANOVA specification instead of regression specification).
+This way, the effect of each dummy reflects the mean value for that category.
+To further aid interpretability, the dependent variable (effect size) was centered around the random-effects meta-analysis estimated overall effect.
+This changes the interpretation of the effect of each dummy, such that it reflects the deviation of that category from the overall effect size as estimated in the random-effects meta-analysis.
+If a dummy variable has a significant effect, that means that that group's mean differs significantly from the overall mean.
+
+```{r, eval = run_everything}
+library(metacart)
+modres <- lapply(processes, function(p){
+  df <- dat[dat$Process == p, ]
+  modmat <- model.matrix(~., df[mods])[,-1]
+  constcols <- colSums(modmat) == 0 | colSums(modmat) == nrow(modmat)
+  constcolnames <- colnames(modmat)[constcols]
+  modmat <- modmat[, !constcols]
+  modmatlist <- as.list(data.frame(modmat))
+  dupcols <- duplicated(modmatlist)
+  modmat <- modmat[, !dupcols]
+  these_dups <- modmatlist[dupcols]
+  modmatlist <- as.list(data.frame(modmat))
+  for(i in 1:length(these_dups)){
+    idnum <- which(duplicated(c(modmatlist, these_dups[i]), fromLast = T))
+    colnames(modmat)[idnum] <- paste0(colnames(modmat)[idnum], ";", names(these_dups)[i])
+  }
+  yi_centered <- df$yi - mlm[[p]]$mod$b[1,1]
+  res <- rma(yi = yi_centered,
+             vi = df$vi,
+             mods = modmat, intercept = F)
+  vifs <- vif(res)
+  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2"),
+                       cbind(
+                         Estimate = c(res$b, res$tau2),
+                         se = c(res$se, res$se.tau2),
+                         ci.lb = c(res$ci.lb, res$tau2-1.96*res$se.tau2),
+                         ci.ub = c(res$ci.ub, res$tau2+1.96*res$se.tau2),
+                         p = c(res$pval, res$QEp)))
+  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
+  tabres[c("ci.lb", "ci.ub")] <- NULL
+  tabres$VIF <- c(vifs$vif, NA)
+  write.csv(tabres, paste0("rma_mods_", p, ".csv"))
+
+  moddat <- data.frame(yi = yi_centered, vi = df$vi, modmat)
+  moddat$study <- 1
+  standardize <- list(center = rep(0, (ncol(moddat)-3)),
+                      scale = rep(1, (ncol(moddat)-3)))
+
+  pma <- brma(yi ~-1+., study = "study", data = moddat, standardize = standardize)
+
+  sumpma <- data.frame(summary(pma)$coefficients)
+  sumpma <- cbind(rownames(sumpma), sumpma)
+  names(sumpma)[1:3] <- c("Parameter", "Estimate", "se")
+  sumpma <- sumpma[!sumpma$Parameter == "tau", ]
+  rownames(sumpma) <- NULL
+  sumpma$CI <- conf_int(lb = sumpma$X2.5., ub = sumpma$X97.5.)
+  pstars <- c("*", "")[as.integer(apply(sumpma[, c("X2.5.", 
+                                                   "X97.5.")], 1, function(x) {
+                                                     sum(sign(x)) == 0
+                                                   })) + 1]
+  sumpma$p <- pstars
+  sumpma[c("sd", grep("^X", names(sumpma), value = T))] <- NULL
+  write.csv(sumpma, paste0("brma_mods_", p, ".csv"))
+  moddatvi <- moddat$vi
+  moddat <- moddat[, -which(colnames(moddat) == "vi")]
+  resmc <- suppressWarnings(metacart::FEmrt(reformulate(mods, response = "yi"), data = df, vi = df$vi))
+  list(rma = tabres,
+       brma = sumpma,
+       mc = resmc)
+})
+names(modres) <- processes
+saveRDS(modres, "modres.RData")
+```
+
+### Classic meta-regression
+
+```{r}
+modres <- readRDS("modres.RData")
+```
+
+Note that analyses containing VIF values greater than 5 should be regarded as problematic, due to multicolinearity.
+This applies to nearly all models.
+
+```{r, results = "asis", eval = FALSE}
+
+htmltools::tagList(
+  lapply(1:length(processes), function(i) {
+    p <- processes[i]
+    tb <- modres[[i]]$rma
+    tb$format <- as.integer(tb$p < .05)
+    formatStyle(
+      formatRound(
+        datatable(
+          tb,
+          rownames = FALSE,
+          caption = paste0("Meta-regression coefficients for ", p),
+          options = list(columnDefs = list(list(
+            targets = 6, visible = FALSE
+          )),
+          "pageLength" = nrow(tb))
+        ),
+        columns = c('Estimate', "se", 'p', "VIF"),
+        digits = 2
+      ),
+      "format",
+      target = "row",
+      backgroundColor = styleEqual(c(0, 1), c('gray', 'white'))
+    )
+  })
+)
+
+```
+
+```{r run-numeric-md, include=FALSE}
+out = NULL
+for (i in 1:length(processes)) {
+  out = c(out, knit_expand('tab_rma_template.rmd'))
+}
+```
+
+`r paste(knit(text = out), collapse = '\n')`
+
+### Bayesian regularized meta-regression:
+
+```{r, results = "asis", eval = FALSE}
+for(i in 1:length(processes)){
+  p <- processes[i]
+  tb <- modres[[i]]$brma
+  tb$format <- as.integer(tb$p == "*")
+  print({datatable(tb, rownames= FALSE, caption = paste0("Bayesian regularized meta-regression coefficients for ", p), options = list(
+              "pageLength" = nrow(tb))) |>
+  formatRound(columns=c('Estimate', 'p'), digits=2)})
+}
+htmltools::tagList(
+  lapply(1:length(processes), function(i) {
+    p <- processes[i]
+    tb <- modres[[i]]$brma
+    tb$format <- as.integer(tb$p < .05)
+    formatStyle(
+      formatRound(
+        datatable(
+          tb,
+          rownames = FALSE,
+          caption = paste0("Bayesian regularized meta-regression coefficients for ", p),
+          options = list(columnDefs = list(list(
+            targets = 7, visible = FALSE
+          )),
+          "pageLength" = nrow(tb))
+        ),
+        columns = c('Estimate', "se"),
+        digits = 2
+      ),
+      "format",
+      target = "row",
+      backgroundColor = styleEqual(c(0, 1), c('gray', 'white'))
+    )
+  })
+)
+
+```
+
+```{r run-numeric-md2, include=FALSE}
+out = NULL
+for (i in 1:length(processes)) {
+  out = c(out, knit_expand('tab_brma_template.rmd'))
+}
+```
+
+`r paste(knit(text = out), collapse = '\n')`
+
+# Conclusion
+
+Meta-analyses revealed limited evidence that overall effects are non-zero in the population,
+except for the processes `r paste0(tb[tb$Parameter == "Overall ES", ]$Process[tb[tb$Parameter == "Overall ES", ]$p < .05], collapse = ", ")`.
+All processes showed significant residual heterogeneity.
+
+To explore whether this heterogeneity could be explained by between-study differences,
+we conducted meta-regression analysis.
+Classic meta-regression analyses were empirically under-identified, however,
+because of the high number of moderators and high multicolinearity among them.
+BRMA analyses were used, which are robust to multicolinearity, and perform variable selection by shrinking regression coefficients towards zero.
+These BRMA analyses revealed no consistent evidence of any significant moderator effect across processes.
+To exclude the possibility that multiple dummies interacted together,
+I conducted additional sensitivity analyses using `metaCART` - a decision-tree based algorithm that inherently accommodates interactions between dummies.
+The `metaCART` analyses also did not find evidence of interaction effects.

### 2022-01-24 manuscript/manuscript.Rmd
Remove intercept from modmat to include first category too

@@
   df <- dat[dat$Process == p, ]
-  modmat <- model.matrix(~., df[mods])[,-1]
+  modmat <- model.matrix(~-1+., df[mods])[,-1]
   constcols <- colSums(modmat) == 0 | colSums(modmat) == nrow(modmat)

### 2022-02-10 manuscript/manuscript.Rmd
forest plot alphabetical

@@
 xname <- paste0("Hedges' g (", p, ")")
-tmp <- df[order(df$vi, decreasing = TRUE), ]
+tmp <- df[order(df$article.code, decreasing = FALSE), ]
 df_es <- data.frame(

### 2022-02-21 manuscript/manuscript.Rmd
update 2022-02-21 13:43:10

@@
 ```{r setup, include=FALSE}
-run_everything = FALSE
+run_everything = TRUE
 library("worcs")
@@
   df <- dat[dat$Process == p, ]
-  modmat <- model.matrix(~-1+., df[mods])[,-1]
+  modmat <- model.matrix(~.-1, df[mods])
   constcols <- colSums(modmat) == 0 | colSums(modmat) == nrow(modmat)

### 2022-02-21 manuscript/manuscript.Rmd
DUmmy coding

@@
 
-As the models contained only categorical variables but no meaningful reference category,
-we estimated a model _without_ an intercept,
-and instead included an equal number of dummies to the number of unique categories (ANOVA specification instead of regression specification).
-This way, the effect of each dummy reflects the mean value for that category.
-To further aid interpretability, the dependent variable (effect size) was centered around the random-effects meta-analysis estimated overall effect.
-This changes the interpretation of the effect of each dummy, such that it reflects the deviation of that category from the overall effect size as estimated in the random-effects meta-analysis.
-If a dummy variable has a significant effect, that means that that group's mean differs significantly from the overall mean.
+To examine the effect of a categorical variable,
+a reference category must be chosen.
+Dummy variables encode the difference between each remaining category and this reference category.
+When examining the results,
+the intercept represents the expected effect size for a study that falls within the reference category for all categorical variables.
+The effect of dummy variables represents the difference of that category with the reference category.
+If a dummy variable has a significant effect, that means that that group's mean differs significantly from the reference category's mean (i.e., from the intercept).
 
@@
   df <- dat[dat$Process == p, ]
-  modmat <- model.matrix(~.-1, df[mods])
+  catvars <- sapply(df, class) == "factor" & names(df) %in% mods
+  df[catvars] <- lapply(df[catvars], function(v){
+    tab <- table(v)
+    relevel(v, ref = names(tab)[which.max(tab)])
+  })
+  refcat <- data.frame(do.call(rbind,lapply(names(df[catvars]), function(n){c(n, levels(df[[n]])[1])})))
+  names(refcat) <- c("Variable", "Reference")
+  modmat <- model.matrix(~., df[mods])
   constcols <- colSums(modmat) == 0 | colSums(modmat) == nrow(modmat)
@@
   }
-  yi_centered <- df$yi - mlm[[p]]$mod$b[1,1]
-  res <- rma(yi = yi_centered,
+  yi_notcentered <- df$yi# - mlm[[p]]$mod$b[1,1]
+  res <- rma(yi = yi_notcentered,
              vi = df$vi,
-             mods = modmat, intercept = F)
+             mods = modmat)
   vifs <- vif(res)
@@
   tabres[c("ci.lb", "ci.ub")] <- NULL
-  tabres$VIF <- c(vifs$vif, NA)
+  tabres$VIF <- c(NA, vifs$vif, NA)
   write.csv(tabres, paste0("rma_mods_", p, ".csv"))
 
-  moddat <- data.frame(yi = yi_centered, vi = df$vi, modmat)
+  moddat <- data.frame(yi = yi_notcentered, vi = df$vi, modmat)
   moddat$study <- 1
@@
 
-  pma <- brma(yi ~-1+., study = "study", data = moddat, standardize = standardize)
+  pma <- brma(yi ~., study = "study", data = moddat, standardize = standardize)
 
@@
        brma = sumpma,
-       mc = resmc)
+       mc = resmc,
+       refcat = refcat)
 })

### 2022-02-21 manuscript/manuscript.Rmd
update 2022-02-21 19:22:02

@@
 ```{r setup, include=FALSE}
-run_everything = TRUE
+run_everything = FALSE
 library("worcs")
@@
 To examine the effect of a categorical variable,
-a reference category must be chosen.
-Dummy variables encode the difference between each remaining category and this reference category.
+we used deviation coding.
+This means that the intercept represents the grand mean accross all categories of the categorical variables.
+Dummy variables encode the difference between each category and this grand mean.
+To ensure model identification, one category is not compared to the grand mean.
+This was always the smallest category in the analyses below.
+
 When examining the results,
-the intercept represents the expected effect size for a study that falls within the reference category for all categorical variables.
-The effect of dummy variables represents the difference of that category with the reference category.
-If a dummy variable has a significant effect, that means that that group's mean differs significantly from the reference category's mean (i.e., from the intercept).
+the intercept represents the overall effect size for the entire sample.
+The effect of dummy variables represents the difference of that category with the overall effect size.
+If a dummy variable has a significant effect, that means that that group's mean differs significantly from the grand mean (i.e., from the intercept).
 
@@
   catvars <- sapply(df, class) == "factor" & names(df) %in% mods
-  df[catvars] <- lapply(df[catvars], function(v){
+  df[catvars] <- lapply(names(df)[catvars], function(n){
+    v <- droplevels(df[[n]])
     tab <- table(v)
-    relevel(v, ref = names(tab)[which.max(tab)])
+    if(length(tab) == 1) return(v)
+    v <- relevel(v, ref = names(tab)[which.min(tab)])
+    conts <- try(contr.sum(length(levels(v))))
+    if(inherits(conts, "try-error")) return(v)
+    conts <- conts[nrow(conts):1, , drop = FALSE]
+    colnames(conts) <- paste0("Mvs", levels(v)[apply(conts, 2, function(x){ which(x == 1) })])
+    tryCatch({contrasts(v) <- conts}, error = function(e){
+      browser()
     })
+    return(v)
+  })
+
   refcat <- data.frame(do.call(rbind,lapply(names(df[catvars]), function(n){c(n, levels(df[[n]])[1])})))
   names(refcat) <- c("Variable", "Reference")
+  mods <- mods[sapply(df[mods], function(x){length(unique(x)) > 1})]
   modmat <- model.matrix(~., df[mods])

### 2022-02-21 manuscript/tab_rma_template.Rmd
update 2022-02-21 19:22:02

@@
+```{r tabref{{i}}, results = 'asis'}
+p <- processes[{{i}}]
+    tb <- modres[[{{i}}]]$refcat
+    # knitr::kable(tb, caption = paste0("Reference category for each variable for process ", p))
+    datatable(
+          tb,
+          rownames = FALSE,
+          caption = paste0("Category not compared to the grand mean for each variable for process ", p))
+```
+
 ```{r tabrma{{i}}, results = 'asis'}

### 2022-02-28 manuscript/manuscript.Rmd
make changes based on elise's email

--- 2022-02-21 manuscript/manuscript.Rmd
@@
 dat <- escalc(measure = "SMD",
-         n1i = dat$number.of.animals.in.control.group,
-         n2i = dat$number.of.animals.in.intervention.group,
-         m1i = dat$mean.control.group,
-         m2i = dat$mean.experimental.group,
-         sd1i = dat$sd.control.group,
-         sd2i = dat$sd.experimental.group,
+         n2i = dat$number.of.animals.in.control.group,
+         n1i = dat$number.of.animals.in.intervention.group,
+         m2i = dat$mean.control.group,
+         m1i = dat$mean.experimental.group,
+         sd2i = dat$sd.control.group,
+         sd1i = dat$sd.experimental.group,
          data = dat)
@@
   tb <- mlm[[i]]$res
+  tb <- rbind(tb, data.frame(Variance = "I2",
+                             estimate.intrcpt = mlm[[i]]$mod$I2,
+                             ci.lb = NA,
+                             ci.ub = NA,
+                             V4 = mlm[[i]]$mod$QEp))
   tb$Process <- processes[i]
@@
 tb <- do.call(rbind, tb)
-tb$CI <- tidySEM::conf_int(lb = tb$ci.lb, ub = tb$ci.ub)
+tb$CI <- NA
+tb$CI[!is.na(tb$ci.lb)] <- tidySEM::conf_int(lb = tb$ci.lb[!is.na(tb$ci.lb)], ub = tb$ci.ub[!is.na(tb$ci.lb)], digits = 2)
 tb[c("ci.lb", "ci.ub")] <- NULL
@@
   vifs <- vif(res)
+  saveRDS(res, paste0("rma_", p, ".RData"))
   tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2"),
@@
   pma <- brma(yi ~., study = "study", data = moddat, standardize = standardize)
-
+  saveRDS(pma, paste0("pma_", p, ".RData"))
   sumpma <- data.frame(summary(pma)$coefficients)
@@
 
+## Subgroup plots
+
+<!-- predictie intervallen van elke categorie een goede manier is om de data te visualiseren en de data duidelijk over te brengen op de lezer. -->
+```{r, eval = run_everything}
+library(ggridges)
+for(p in processes){
+  res <- readRDS(paste0("pma_", p, ".RData"))
+  pred <- pema:::predict.brma(res, newdata = res$X, type = "samples")
+  for(v in c("ssri", "freq", "disease", "species", "test")){
+    print(paste0(v, "_", p))
+    catdf <- res$X[, startsWith(colnames(res$X), v), drop = F]
+    splt <- apply(catdf, 1, which.max) + 1
+    splt[rowSums(catdf == 0) == ncol(catdf)] <- 1
+    labs <- c(modres[[p]]$refcat$Reference[modres[[p]]$refcat$Variable == v],
+              unique(gsub(".", "", gsub(v, "", grep(paste0("^", v), colnames(res$X), value = T)), fixed = TRUE)))
+    splt <- factor(splt, labels = labs)
+    df_plot <- do.call(rbind, lapply(levels(splt), function(l){
+      data.frame(Value = as.vector(pred[splt == l, ]),
+                 Group = l)
+    }))
+    meds <- tapply(df_plot$Value, df_plot$Group, median)
+    postplot <- ggplot(df_plot, aes(x = Value, y = Group)) +
+      geom_density_ridges(scale = 1, alpha = 0) +
+      geom_segment(data = data.frame(x = meds, xend = meds, y = 1:length(meds), yend = (2:(length(meds)+1))), aes(x = x, xend = xend, y = y, yend = yend), inherit.aes = F, colour = "skyblue3", size = 1) +
+      theme_bw() +
+      scale_y_discrete(expand =c(0,0))+
+      labs(title = p,
+           x = paste0("Posterior predicted effect size"),
+           y = v)
+    ggsave(filename = paste0("group_plot_", v, "_", p, ".png"), plot = postplot, device = "png")
+  }
+}
+```
+
+```{r}
+out = NULL
+vars <- c("ssri", "freq", "disease", "species", "test")
+plotnames <- paste0(
+  "group_plot_", 
+  rep(vars, length(processes)),
+  "_",
+  rep(processes, each = length(vars)),
+  ".png")
+
+for(i in seq(plotnames)){
+  plotname = plotnames[i]
+  out = c(out, knit_expand('plot_template.rmd'))
+}
+
+```
+
+`r paste(knit(text = out), collapse = '\n')`
+
 # Conclusion

### 2022-03-01 manuscript/manuscript.Rmd
update 2022-03-01 17:37:58

@@
 If a dummy variable has a significant effect, that means that that group's mean differs significantly from the reference category's mean (i.e., from the intercept).
+The analyses below used the following reference categories:
+
+```{r}
+refcat <- structure(list(Variable = c("ssri", "freq", "disease", "species", "test"
+), Reference = c("FLX", "chronic", "stress", "rat", "CF")), class = "data.frame", row.names = c(NA, -5L))
+
+datatable(
+  refcat,
+  rownames = FALSE,
+  caption = "Reference category for each variable")
+```
 
@@
   df <- dat[dat$Process == p, ]
-  catvars <- sapply(df, class) == "factor" & names(df) %in% mods
-  df[catvars] <- lapply(df[catvars], function(v){
-    tab <- table(v)
-    relevel(v, ref = names(tab)[which.max(tab)])
+  df[refcat$Variable] <- lapply(refcat$Variable, function(n){
+    v <- df[[n]]
+    v <- relevel(v, ref = refcat$Reference[refcat$Variable == n])
+    droplevels(v)
   })
-  refcat <- data.frame(do.call(rbind,lapply(names(df[catvars]), function(n){c(n, levels(df[[n]])[1])})))
-  names(refcat) <- c("Variable", "Reference")
-  modmat <- model.matrix(~., df[mods])
+  # refcat <- data.frame(do.call(rbind,lapply(names(df[catvars]), function(n){c(n, levels(df[[n]])[1])})))
+  # names(refcat) <- c("Variable", "Reference")
+  df_mods <- df[mods]
+  constcols <- sapply(df_mods, function(i){length(unique(i))}) == 1
+  df_mods <- df_mods[, !constcols, drop = FALSE]
+  modmat <- model.matrix(~., df_mods)
   constcols <- colSums(modmat) == 0 | colSums(modmat) == nrow(modmat)
@@
        brma = sumpma,
-       mc = resmc,
-       refcat = refcat)
+       mc = resmc)
 })
@@
 ```{r, eval = run_everything}
+refcat <- structure(list(Variable = c("ssri", "freq", "disease", "species", "test"
+), Reference = c("FLX", "chronic", "stress", "rat", "CF")), class = "data.frame", row.names = c(NA, 
+-5L))
 library(ggridges)
@@
   pred <- pema:::predict.brma(res, newdata = res$X, type = "samples")
-  for(v in c("ssri", "freq", "disease", "species", "test")){
-    print(paste0(v, "_", p))
+  vars <- c("ssri", "freq", "disease", "species", "test")
+  vars <- vars[sapply(vars, function(v){any(grepl(v, colnames(res$X)))})]
+  for(v in vars){
     catdf <- res$X[, startsWith(colnames(res$X), v), drop = F]
@@
     splt[rowSums(catdf == 0) == ncol(catdf)] <- 1
-    labs <- c(modres[[p]]$refcat$Reference[modres[[p]]$refcat$Variable == v],
+    labs <- c(refcat$Reference[refcat$Variable == v],
               unique(gsub(".", "", gsub(v, "", grep(paste0("^", v), colnames(res$X), value = T)), fixed = TRUE)))

### 2022-03-01 manuscript/manuscript.Rmd
update 2022-03-01 18:06:36

@@
 ```{r setup, include=FALSE}
-run_everything = FALSE
+run_everything = TRUE
+sensitivity = FALSE
+sens_papers <- "{{sens_study}}" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
 library("worcs")
@@
 load_data()
+if(sensitivity){
+  dat <- dat[!dat$article.code %in% sens_papers, ]
+}
 dat$Process <- ordered(dat$Process, levels = unique(dat$Process))
@@
 
+```{r, results="asis"}
+print("**This is a sensitivity analysis; the study {{sens_study}} has been removed from the data.")
+```
+
 <!--   Information regarding this data file for the SR fear learning & SSRIs -->
@@
 mlm <- lapply(processes, function(p){
+  print(p)
   df <- dat[dat$Process == p, ]
+  if(nrow(df) == 0) return(NULL)
   #Conduct meta-analyses
@@
 tb <- lapply(1:length(processes), function(i){
+  if(is.null(mlm[[i]])) return(NULL)
   tb <- mlm[[i]]$res
@@
   df <- dat[dat$Process == p, ]
+  if(nrow(df) == 0) return(NULL)
   df[refcat$Variable] <- lapply(refcat$Variable, function(n){
@@
   p <- processes[i]
+  if(is.null(modres[[i]])) next
   tb <- modres[[i]]$brma
@@
 for(p in processes){
+  if(is.null(modres[[p]])) next
   res <- readRDS(paste0("pma_", p, ".RData"))

### 2022-03-02 manuscript/manuscript.Rmd
update 2022-03-02 15:25:16

@@
 
-```{r, results="asis"}
-print("**This is a sensitivity analysis; the study {{sens_study}} has been removed from the data.")
+```{r, results = "asis"}
+cat("**This is a sensitivity analysis; the study {{sens_study}} has been removed from the data.**")
 ```
@@
 modres <- lapply(processes, function(p){
+  print(p)
   df <- dat[dat$Process == p, ]
@@
   constcolnames <- colnames(modmat)[constcols]
-  modmat <- modmat[, !constcols]
+  modmat <- modmat[, !constcols, drop = FALSE]
   modmatlist <- as.list(data.frame(modmat))
   dupcols <- duplicated(modmatlist)
-  modmat <- modmat[, !dupcols]
+  modmat <- modmat[, !dupcols, drop = FALSE]
   these_dups <- modmatlist[dupcols]
@@
 
-  pma <- brma(yi ~., study = "study", data = moddat, standardize = standardize)
+  pma <- try({brma(yi ~., study = "study", data = moddat, standardize = standardize)})
+  if(inherits(pma, "try-error")){
+    pma <- NULL
+    sumpma <- data.frame(NA, NA)
+  } else {
     saveRDS(pma, paste0("pma_", p, ".RData"))
@@
   write.csv(sumpma, paste0("brma_mods_", p, ".csv"))
+  }
+
   moddatvi <- moddat$vi

### 2022-03-02 manuscript/sensitivity_Camp20121.Rmd
update 2022-03-02 15:25:16

--- 2022-03-01 manuscript/manuscript.Rmd
@@
 run_everything = TRUE
-sensitivity = FALSE
-sens_papers <- "{{sens_study}}" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
+sensitivity = TRUE
+sens_papers <- "Camp 2012 (1)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
 library("worcs")
@@
 
-```{r, results="asis"}
-print("**This is a sensitivity analysis; the study {{sens_study}} has been removed from the data.")
+```{r, results = "asis"}
+cat("**This is a sensitivity analysis; the study Camp 2012 (1) has been removed from the data.**")
 ```

### 2022-03-02 manuscript/sensitivity_Camp20122.Rmd
update 2022-03-02 15:25:16

--- 2022-03-02 manuscript/sensitivity_Camp20121.Rmd
@@
 sensitivity = TRUE
-sens_papers <- "Camp 2012 (1)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
+sens_papers <- "Camp 2012 (2)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
 library("worcs")
@@
 ```{r, results = "asis"}
-cat("**This is a sensitivity analysis; the study Camp 2012 (1) has been removed from the data.**")
+cat("**This is a sensitivity analysis; the study Camp 2012 (2) has been removed from the data.**")
 ```

### 2022-03-02 manuscript/sensitivity_Camp20123.Rmd
update 2022-03-02 15:25:16

--- 2022-03-02 manuscript/sensitivity_Camp20122.Rmd
@@
 sensitivity = TRUE
-sens_papers <- "Camp 2012 (2)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
+sens_papers <- "Camp 2012 (3)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
 library("worcs")
@@
 ```{r, results = "asis"}
-cat("**This is a sensitivity analysis; the study Camp 2012 (2) has been removed from the data.**")
+cat("**This is a sensitivity analysis; the study Camp 2012 (3) has been removed from the data.**")
 ```

### 2022-03-02 manuscript/sensitivity_Camp20124.Rmd
update 2022-03-02 15:25:16

--- 2022-03-02 manuscript/sensitivity_Camp20123.Rmd
@@
 sensitivity = TRUE
-sens_papers <- "Camp 2012 (3)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
+sens_papers <- "Camp 2012 (4)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
 library("worcs")
@@
 ```{r, results = "asis"}
-cat("**This is a sensitivity analysis; the study Camp 2012 (3) has been removed from the data.**")
+cat("**This is a sensitivity analysis; the study Camp 2012 (4) has been removed from the data.**")
 ```

### 2022-03-02 manuscript/sensitivity_Fitzgerald2015.Rmd
update 2022-03-02 15:25:16

--- 2022-03-02 manuscript/sensitivity_Camp20124.Rmd
@@
 sensitivity = TRUE
-sens_papers <- "Camp 2012 (4)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
+sens_papers <- "Fitzgerald 2015" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
 library("worcs")
@@
 ```{r, results = "asis"}
-cat("**This is a sensitivity analysis; the study Camp 2012 (4) has been removed from the data.**")
+cat("**This is a sensitivity analysis; the study Fitzgerald 2015 has been removed from the data.**")
 ```

### 2022-03-02 manuscript/sensitivity_Gottschalk2018.Rmd
update 2022-03-02 15:25:16

--- 2022-03-02 manuscript/sensitivity_Camp20124.Rmd
@@
 sensitivity = TRUE
-sens_papers <- "Camp 2012 (4)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
+sens_papers <- "Gottschalk 2018" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
 library("worcs")
@@
 ```{r, results = "asis"}
-cat("**This is a sensitivity analysis; the study Camp 2012 (4) has been removed from the data.**")
+cat("**This is a sensitivity analysis; the study Gottschalk 2018 has been removed from the data.**")
 ```

### 2022-03-02 manuscript/sensitivity_Ju2017.Rmd
update 2022-03-02 15:25:16

--- 2022-03-02 manuscript/sensitivity_Camp20124.Rmd
@@
 sensitivity = TRUE
-sens_papers <- "Camp 2012 (4)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
+sens_papers <- "Ju 2017" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
 library("worcs")
@@
 ```{r, results = "asis"}
-cat("**This is a sensitivity analysis; the study Camp 2012 (4) has been removed from the data.**")
+cat("**This is a sensitivity analysis; the study Ju 2017 has been removed from the data.**")
 ```

### 2022-03-02 manuscript/sensitivity_Xiong20151.Rmd
update 2022-03-02 15:25:16

--- 2022-03-02 manuscript/sensitivity_Ju2017.Rmd
@@
 sensitivity = TRUE
-sens_papers <- "Ju 2017" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
+sens_papers <- "Xiong 2015 (1)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
 library("worcs")
@@
 ```{r, results = "asis"}
-cat("**This is a sensitivity analysis; the study Ju 2017 has been removed from the data.**")
+cat("**This is a sensitivity analysis; the study Xiong 2015 (1) has been removed from the data.**")
 ```

### 2022-03-02 do_sensitivity.R

@@ -1,0 +1,10 @@
+sens <- c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (2)") # "Xiong 2015 (1)",  does not work
+man <- readLines("manuscript/manuscript.Rmd")
+man[grepl("sensitivity = FALSE", man)] <- "sensitivity = TRUE"
+for(s in sens){
+  tmp <- man
+  tmp[grepl("{{sens_study}}", tmp, fixed = TRUE)] <- gsub("{{sens_study}}", s, tmp[grepl("{{sens_study}}", tmp, fixed = TRUE)], fixed = TRUE)
+  fnam <- file.path("manuscript", paste0("sensitivity_", gsub("[\\(\\) ]", "", s), ".Rmd"))
+  writeLines(tmp, fnam)
+  rmarkdown::render(fnam)
+}

### 2022-03-14 manuscript/manuscript.Rmd
remove verma

@@
 maxz <- max(zscores)
-dat <- dat[-which.max(zscores), ]
+dat <- dat[-which.max(abs(zscores)), ]
 # De article code geeft de unieke ID van elk artikel en daarbinnen ook de experimenten aan.
